---
title: "Human Psoriasis Proportion Analyses"
author: "Larry Chen"
date: "2023-01-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat)
library(SeuratObject)
library(patchwork)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tibble)
library(sessioninfo)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

## Read in needed objects and files

```{r load-files}
cheng_ife_cyc_int_metadata = read.table("C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/cheng_ife/cheng_ife_cyc_int/cheng_ife_cyc_int_metadata.txt")
cheng_ife_cyc_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/cheng_ife/cheng_ife_cyc_int/cheng_ife_cyc_int.Rds")
cheng_ife = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/cheng_ife/cheng_ife.Rds")
```

# 5: PROPORTION ANALYSIS

## Proportion of cycling cells that are basal/spinous

First, we generate a table of proportions of basal and spinous cells that are cycling, with each cell representing the proportion of cycling cells that are either basal or spinous, for each sample.

This is done by calculating the proportion of cells in res 0.1 clusters 0 (cycling spinous) and 1 (cycling basal) in each sample.

```{r cyc-prop-table}
# Proportion analysis
cyc_prop_table = prop.table(table(cheng_ife_cyc_int_metadata[,"integrated_snn_res.0.1"],cheng_ife_cyc_int_metadata[,"sample"]),margin=2)
rownames(cyc_prop_table) = c("Spinous","Basal")
```

```{r display-cyc-prop-table}
cyc_prop_table
```

Here, we create a melted version of the table showing the proportion of cycling cells that are either spinous or basal, for each sample.

```{r cyc_prop_table_df}
cyc_prop_table_df = melt(cyc_prop_table)
colnames(cyc_prop_table_df) = c("Layer","Sample","Proportion")
cyc_prop_table_df$Condition = c(rep("Healthy",6),rep("Pso",6),rep("Healthy",6))
```

```{r display-cyc_prop_table_df}
cyc_prop_table_df
```

#### Saving Boxplots

This melted table is then used to generate box plots.

```{r melt-frame}
setwd('C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/')
cyc_prop_table_df_basal = subset(cyc_prop_table_df,Layer=="Basal")
g <- ggplot(cyc_prop_table_df_basal, aes(Condition, Proportion)) + geom_boxplot() + 
      labs(x='Layer', y='Proportion Basal of Cycling Cells',title='Cycling Cell Analysis') 
ggsave(plot=g,"cheng_ife_cyc_int_proportion_basal_boxplot.pdf",width = 5, height=5, dpi=300, useDingbats=F)

cyc_prop_table_df_spn = subset(cyc_prop_table_df,Layer=="Spinous")
g <- ggplot(cyc_prop_table_df_spn, aes(Condition, Proportion)) + geom_boxplot() + 
  labs(x='Layer', y='Proportion Spinous of Cycling Cells',title='Cycling Cell Analysis') 
ggsave(plot=g,"cheng_ife_cyc_int_proportion_spn_boxplot.pdf",width = 5, height=5, dpi=300, useDingbats=F)
```

## Proportion of basal/spinous cells that are cycling

The overall equation for calculating the proportion of Basal/Spinous cells that are cycling is as follows:

$$
Proportion\,of\,Basal/Spinous\,Cells\,that\,are\,Cycling = \dfrac{Cycling\,Basal/Spinous\,Cells}{All\,Basal/Spinous\,Cells}
$$

The total number of basal/spinous cells is calculated by adding the number of cycling basal/spinous cells to the number of non-cycling basal/spinous cells identified in cheng_ife_cyc_int.

Since we have already identified the basal and spinous cells that are cycling, what's left to do is to identify non-cycling basal spinous cells.

## Identifying non-cycling basal and spinous cells

Here, we identify non-cycling basal and spinous cells within the cheng_ife dataset.

```{r identify-noncyc-basal-spinous-cells}
Idents(cheng_ife) = "integrated_snn_res.0.4"
DimPlot(cheng_ife, reduction = "umap", label = TRUE)
```

The non-cycling spinous cells were identified as clusters 1,0,8,9; and the non-cycling basal cells were identified as clusters 2,3,4. Cluster 6 represents granular cells.

```{r-col17a1-krt10-ivl-featureplot-cheng_ife}
DefaultAssay(cheng_ife) = "RNA"
FeaturePlot(cheng_ife, features = c("COL17A1", "KRT10", "IVL"))
DefaultAssay(cheng_ife) = "integrated"
```

### Calculating proportions

We first create a table with the per sample proportions of basal, cycling, granular, and spinous cells.

```{r freq-prop-anal}
#FREQUENCY PROPORTION ANALYSIS
cheng_ife_metadata = read.csv("C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/cheng_ife/cheng_ife_metadata.csv", row.names = 1)

#creating simple subpopulation annotations from integrated_snn_res.0.4 cluster identities
cheng_ife_metadata = cheng_ife_metadata %>% mutate(kc_subpop =
                     case_when(integrated_snn_res.0.4 %in% c(1,0,8,9) ~ "Basal", 
                               integrated_snn_res.0.4 %in% c(2,3,4) ~ "Spinous",
                               integrated_snn_res.0.4 %in% c(5,7) ~ "Cycling",
                               integrated_snn_res.0.4 == 6 ~ "Granular")
)
prop.table(table(cheng_ife_metadata$kc_subpop, cheng_ife_metadata$sample), margin=2)
```

We then reassign the cycling cells as either cycling spinous or cycling basal cells, by matching them to their cheng_ife_cyc_int integrated_snn_res.0.1 cluster identities.

```{r label-cyc-spinous-basal}
# Label cycling subpopulations from cheng_ife_cyc_int
kc_subpop_cyc = cheng_ife_metadata$kc_subpop
res0.1_clus = 0:1
res0.1_subpop = c("Spinous_Cycling","Basal_Cycling")
for (i in 1:2)
{
  clus_id = res0.1_clus[i]
  cell_id = rownames(cheng_ife_cyc_int_metadata)[which(cheng_ife_cyc_int_metadata[,"integrated_snn_res.0.1"]==clus_id)]
  print(length(cell_id))
  kc_subpop_cyc[match(cell_id,rownames(cheng_ife_metadata))] = res0.1_subpop[i]
}
cheng_ife_metadata$kc_subpop_cyc = kc_subpop_cyc
```

We then classify cells as being from either psoriatic or healthy samples.

```{r simple-sample}
# label condition
cheng_sample = c("pso14", "p48epi", "p49epi", "s11", "scalp26", "scalp32", "abd4", 
                 "br41epi", "br53epi")
cheng_condition = c(rep("Pso",3),rep("Healthy",6))
cheng_sample_vector = cheng_ife_metadata$sample
for (i in 1:length(cheng_sample))
{
  clus_id = cheng_sample[i]
  cell_id = rownames(cheng_ife_metadata)[which(cheng_ife_metadata$sample==cheng_sample[i])]
  cheng_sample_vector[which(cheng_ife_metadata$sample==clus_id)] = cheng_condition[i]
}
```

####saving updated metadata

```{r save-metadata-cheng_ife, eval_false}
setwd('C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/cheng_ife')
cheng_ife_metadata$condition = cheng_sample_vector

write.table(cheng_ife_metadata,file="cheng_ife_metadata_cycling_subpopulation.txt",sep="\t",row.names=T,col.names=T)

ife_subpop_data = cheng_ife_metadata[,c("sample","kc_subpop_cyc","condition")]
```

####Calculations

Finally, we calculate the proportion of basal/spinous cells that are cycling, for each sample.

```{r calc-props}
# Calculate subpop proportions
subpop_table = table(cheng_ife_metadata$kc_subpop_cyc,cheng_ife_metadata$sample) #count table 
pct_basal_cycling = apply(subpop_table, 2, function(x) {x[2]/(x[2]+x[1])})
pct_spinous_cycling = apply(subpop_table, 2, function(x) {x[5]/(x[5]+x[4])})

t.test(pct_basal_cycling[c(1:3,7:9)],pct_spinous_cycling[c(1:3,7:9)])
t.test(pct_spinous_cycling[c(1:3,7:9)],pct_spinous_cycling[4:6])
ife_subpop_df = melt(ife_subpop_data)
```

### Saving boxplots

Showing proportion of basal/spinous cells that are cycling in each condition

```{r prop-boxplots}
setwd('C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/')
subpop_prop_table_df = data.frame(pct_basal_cycling,pct_spinous_cycling)
subpop_prop_table_df$condition = c(rep("Healthy",3),rep("Pso",3),rep("Healthy",3))
g <- ggplot(subpop_prop_table_df, aes(condition, pct_basal_cycling)) + geom_boxplot() + 
  labs(x='Condition', y='Proportion Cycling Basal Cells',title='Cycling Cell Analysis') 
ggsave(plot=g,"cheng_ife_cyc_int_basal_prop_cycling_boxplot.pdf",width = 5, height=5, dpi=300, useDingbats=F)

cyc_prop_table_df_spn = subset(cyc_prop_table_df,Layer=="Spinous")
g <- ggplot(subpop_prop_table_df, aes(condition, pct_spinous_cycling)) + geom_boxplot() + 
  labs(x='Condition', y='Proportion Cycling Spinous Cells',title='Cycling Cell Analysis') 
ggsave(plot=g,"cheng_ife_cyc_int_spn_prop_cycling_boxplot.pdf",width = 5, height=5, dpi=300, useDingbats=F)
```

## Final Results

```{r show-final-results}
print(subpop_prop_table_df)
```
