---
title: "Processing pso_cheng_ife"
author: "Larry Chen"
date: "2023-01-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package. 
```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r load-packages, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
#library(Seurat)
#library(SeuratObject)
library(patchwork)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tibble)
library(sessioninfo)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

# 2. ISOLATING IFE CELLS FROM PSORIATIC SAMPLES

## Pso_cheng preprocessing

```{r load-pso_cheng_no_int}
# Merge IFE psoriasis and IFE healthy
# Import and Preprocess data
pso_cheng_no_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/psoriasis/hu/pso_cheng/pso_cheng.Rds")
DefaultAssay(pso_cheng_no_int) = "RNA"
```

```{r normalize-pso_cheng_no_int}
hu.list <- SplitObject(pso_cheng_no_int, split.by = "sample")


# Normalize all objects
for (i in 1:length(hu.list)) {
    hu.list[[i]] <- NormalizeData(hu.list[[i]], verbose = FALSE)
    hu.list[[i]] <- FindVariableFeatures(hu.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
    print(i)
}
```

```{r integrate-pso_cheng_no_int, message = FALSE}
reference.list <- hu.list
hu.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

pso_cheng <- IntegrateData(anchorset = hu.anchors, dims = 1:30)
```

### Seurat Data Processing

```{r scale-pso_cheng}
pso_cheng <- ScaleData(pso_cheng, verbose = FALSE)
pso_cheng <- RunPCA(pso_cheng, npcs = 30, verbose = FALSE)
pso_cheng <- RunUMAP(pso_cheng, reduction = "pca", dims = 1:30)
```

### Clustering

Clusters are generated at resolutions 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, and 1.2 to help with isolating cells.

```{r cluster-pso_cheng}
DefaultAssay(pso_cheng) = "integrated"
all_res = c(0.1,0.2,0.4,0.6,0.8,1.0,1.2)
pso_cheng <- FindNeighbors(pso_cheng, dims = 1:30, verbose = T)

for (i in all_res){
  pso_cheng <- FindClusters(pso_cheng, resolution = i, verbose = FALSE)
}
```

### Save pso_cheng

```{r save-pso_cheng, eval = FALSE}
saveRDS(pso_cheng, "C:/Users/Ji Lab/Documents/JID manuscript/psoriasis/hu/pso_cheng/pso_cheng.Rds")
```

## Generating UMAPs, Feature Plots, and Marker Lists

These tools were used to identify clusters. UMAPs, Feature Plots, and Marker Lists are generated for every cluster resolution.

### UMAPS

```{r umap-pso_cheng}
#Generating and Saving UMAPs
all_res = c(0.1,0.2,0.4,0.6,0.8,1.0,1.2)
setwd('C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/pso_cheng')
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(pso_cheng) = paste("integrated_snn_res.",res,sep="")
  png(paste("pso_cheng_UMAP",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(pso_cheng, reduction="umap", label=T, pt.size = 1)
  print(p)
  dev.off()
}
```

### Feature Plots

```{r feature-plot-pso_cheng, eval = FALSE}
#Generating and Saving Feature Plots
DefaultAssay(pso_cheng) = "RNA"
genes = list(c("KRT10",'COL17A1'),c("LOR",'FLG','IVL','KLK7'),c("MKI67",'PCNA','TOP2A'), c("ITGA6", "ITGB4", "ITGB1", "KRT14", "KRT5",'COL17A1'), c("KRT79","EPCAM", "SOX9"))
setwd('C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/pso_cheng')
for (i in 1:length(genes))
{
  png(paste("pso_cheng_",paste(genes[[i]], collapse = '.'),"_noaxes_nolegend.png", sep=""), units = "in", height = 6, width = 10, res=300)
  p= FeaturePlot(object = pso_cheng, features = genes[[i]], cols = c("lightgrey", "blue"), pt.size = 1)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

### Marker Lists

```{r markers-pso_cheng, message = FALSE, eval = FALSE}
DefaultAssay(pso_cheng) = "RNA"
for (i in all_res){
  Idents(pso_cheng) = paste("integrated_snn_res.", i, sep = '')
  pso_cheng.markers = FindAllMarkers(pso_cheng, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  write.csv(pso_cheng.markers, paste0("C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/pso_cheng/pso_cheng.markers_",i,".csv"))
}
```

## Subsetting IFE cells

Using the generated feature maps, In pso_cheng, clusters 0-5, and 8 \@ resolution 0.4 were identified as interfollicular epidermal (IFE) cells.

```{r subset-dimplot-pso_cheng}
Idents(pso_cheng) = "integrated_snn_res.0.4"
DimPlot(pso_cheng, label = TRUE)
```

```{r subset-feature-pso_cheng}
DefaultAssay(pso_cheng) = "RNA"
FeaturePlot(pso_cheng, features = c('LHX2','KRT17','AWAT2','DCD','COL1A1','MLANA','VWF','CD3E','CD207','CD163'))
```

```{r subset-pso_cheng}
DefaultAssay(pso_cheng) = "integrated"
Idents(pso_cheng) = "integrated_snn_res.0.4"
pso_cheng_ife = subset(pso_cheng, idents = c(0:5,8))
```

### Saving object

```{r save-pso_cheng_ife, eval = FALSE}
saveRDS(pso_cheng_ife, "C:/Users/Ji Lab/Documents/JID manuscript/Psoriasis/hu/pso_cheng/pso_cheng_ife/pso_cheng_ife.Rds")
```