---
title: "Integrating ns_int"
author: "Larry Chen"
date: "2023-01-05"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r load-packages, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
```
```{r Session-Info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```
```{r, include = FALSE}
ns_int = readRDS('C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int.Rds')
```
## load datasets

```{r load-individual-datasets, eval = FALSE}
ns_tabib = readRDS("/oak/stanford/groups/khavari/users/andrewji/NS_datasets/analysis/tabib_data/ns_tabib.Rds")
ns_cheng = readRDS("/oak/stanford/groups/khavari/users/andrewji/NS_datasets/analysis/cheng_data/ns_body.Rds")
ns_taka = readRDS("/oak/stanford/groups/khavari/users/andrewji/seurat_obj/rt_all.Rds")
norm_update = readRDS("/oak/stanford/groups/khavari/users/andrewji/normal_skin/norm/norm_update_no_rp.Rds")
```

## Preprocess datasets

```{r, eval = FALSE}
norm_update$sample = norm_update$patient
ns_taka$sample = ns_taka$orig.ident
ns_tabib$sample = ns_tabib$orig.ident
norm_update[["percent.mt"]] <- PercentageFeatureSet(norm_update, pattern = "^MT-")
ns_taka = subset(ns_taka, nFeature_RNA>200)
```

### assign dataset identities

```{r, eval = FALSE}
ns_taka$dataset = rep("RT",ncol(ns_taka))
norm_update$dataset = rep("AJ",ncol(norm_update))
ns_tabib$dataset = rep("TT",ncol(ns_tabib))
ns_cheng$dataset = rep("JC",ncol(ns_cheng))
```
### merge datasets
```{r, eval = FALSE}
all_obj = list(norm_update,ns_tabib,ns_cheng,ns_taka)
allnames = c("AJ","TT","JC","RT")

ns_all <- merge(norm_update, y = unlist(all_obj[2:4]), add.cell.ids = allnames, project = "ns_all")
```
### normalize datasets
```{r, eval = FALSE}
ns.list <- SplitObject(ns_all, split.by = "sample")

for (i in 1:length(ns.list)) {
    ns.list[[i]] <- NormalizeData(ns.list[[i]], verbose = FALSE)
    ns.list[[i]] <- FindVariableFeatures(ns.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```
## Integrate datasets
```{r, eval = FALSE}
reference.list <- ns.list
ns.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

ns_int <- IntegrateData(anchorset = ns.anchors, dims = 1:30)
DefaultAssay(ns_int) <- "integrated"
```
### scale integrated dataset
```{r, eval = FALSE}

ns_int <- ScaleData(ns_int, verbose = FALSE)
ns_int <- RunPCA(ns_int, npcs = 30, verbose = FALSE)
ns_int <- RunUMAP(ns_int, reduction = "pca", dims = 1:30)
```
###clustering
```{r, eval = FALSE}

ns_int <- FindNeighbors(ns_int, dims = 1:30, verbose = T)
ns_int <- FindClusters(ns_int, resolution = 0.1, verbose = FALSE)
#ns_int <- FindClusters(ns_int, resolution = 0.15, verbose = FALSE)
ns_int <- FindClusters(ns_int, resolution = 0.2, verbose = FALSE)
#ns_int <- FindClusters(ns_int, resolution = 0.25, verbose = FALSE)
#ns_int <- FindClusters(ns_int, resolution = 0.3, verbose = FALSE)
ns_int <- FindClusters(ns_int, resolution = 0.4, verbose = FALSE)
ns_int <- FindClusters(ns_int, resolution = 0.6, verbose = FALSE)
ns_int <- FindClusters(ns_int, resolution = 0.8, verbose = FALSE)
```
###save file
```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int")
saveRDS(ns_int, file="ns_int.Rds") 
```
##Graphing
###umaps
```{r, eval = FALSE}
p1 <- DimPlot(ns_int, reduction = "umap", group.by = "sample")

setwd("/scratch/groups/khavari/users/andrewji/ns_int/plots")
```
```{r, eval = FALSE}
png("ns_int_labelby_sample.png", units = "in", height = 5, width = 8, res=300)
print(p1)
dev.off()
png("ns_int_labelby_dataset.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int, reduction = "umap", group.by = "dataset")
dev.off()
png("ns_int_labelby_subcell.png", units = "in", height = 5, width = 10, res=300)
DimPlot(ns_int, reduction = "umap", group.by = "subcell")
dev.off()
png("ns_int_labelby_subcell.png", units = "in", height = 5, width = 10, res=300)
DimPlot(ns_int, reduction = "umap", group.by = "subcell")
dev.off()
```
#### split by samples
```{r, echo = FALSE}
DimPlot(ns_int, reduction = "umap", group.by = "sample")
```
#### split by datasets
```{r, echo = FALSE}
DimPlot(ns_int, reduction = "umap", group.by = "dataset")
```
#### highlighting specific datasets
#####defining subsets
```{r}
Idents(ns_int) = 'dataset'
AJ_cells = WhichCells(ns_int, idents = c('AJ'))
JC_cells = WhichCells(ns_int, idents = c('JC'))
RT_cells = WhichCells(ns_int, idents = c('RT'))
TT_cells = WhichCells(ns_int, idents = c('TT'))
```
```{r}
DimPlot(ns_int, reduction = "umap", cols = 'lightgray', cells.highlight = AJ_cells)
```
```{r}
DimPlot(ns_int, reduction = "umap", cols = 'lightgray', cells.highlight = JC_cells)
```
```{r}
DimPlot(ns_int, reduction = "umap", cols = 'lightgray', cells.highlight = RT_cells)
```
```{r}
DimPlot(ns_int, reduction = "umap", cols = 'lightgray', cells.highlight = TT_cells)
```
### graphing subcell types of interest
```{r, eval = FALSE}
subcell_order = c("Bas_I", "Bas_II", "Basal_III", "Cyc_I", "Cyc_II", "Cyc_III", 
"Ecc_II", "Endothelial Cell", "Fibroblast", "Grn", "HF", "IB", 
"Inf_I", "Inf_II", "Inf_III", "Inf_IV", "Keratinocyte", "LC", 
"Melanocyte", "Mtx_I", "Mtx_II", "Multiplet", "N_Cyc", "OB", 
"PS_Cyc", "SG_I", "SG_II", "Spn_I", "Spn_IFN", "Spn_II", "Spn_III", 
"ASDC", "CD1C", "CLEC9A", "Ecc_I", "Mac", "MDSC", "PDC", "Tcell", 
"B Cell", "IRS", "NK", "SB", "Spn_RDX", "Multi", "N_Basal")
Idents(ns_int) = "subcell"
```

```{r, eval = FALSE}
cells_highlight = WhichCells(ns_int, idents = subcell_order)
png("ns_int_labelby_subcell_noNA.png", units = "in", height = 5, width = 10, res=300)
DimPlot(ns_int, reduction = "umap",cells = cells_highlight)
dev.off()
png("ns_int_labelby_subcell_noNA_label.png", units = "in", height = 5, width = 10, res=300)
DimPlot(ns_int, reduction = "umap",cells = cells_highlight, label=T)
dev.off()

png("ns_int_labelby_percentmt.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int, features = "percent.mt")
dev.off()
png("ns_int_labelby_nUMI.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int, features = "nCount_RNA")
dev.off()
png("ns_int_labelby_nFeature.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int, features = "nFeature_RNA")
dev.off()
```


###umaps at different resolutions
```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(ns_int) = paste("integrated_snn_res.",res,sep="")
  png(paste("ns_int_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(ns_int, reduction="umap", label=T, do.return = T, pt.size = 0.1)
  print(p)
  dev.off()
}
```

```{r}
Idents(ns_int) = 'integrated_snn_res.0.6'
DimPlot(ns_int, reduction = 'umap', label = T)
```
### gene feature plots
```{r, eval = FALSE}
genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207",
	"CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1",
	"KRT23","KRT25","KRT6A","KRT16","KRT17","PPARG","DIO2","COMP","FGF7","COL17A1","TP63","PTN","SAT1","SOX4","KLF5","TNC",
	"PTHLH","MT1X","MT1G","MT1H","MT1E","SFRP1","DMKN","ZNF750","IVL","SOSTDC1","FGF18","IL37","IL1F10","IL36RN","IL1RN",
	"MDK","LGALS1","CD151","ITGB1","MKI67","LUM","COL6A1","SOX2","DHRS9","LCE1E","PIP")
```

```{r, eval = FALSE}
#genes = "MT-CYB"
genes_match = genes[genes %in% rownames(ns_int)]

for (i in 1:length(genes_match))
{
  png(paste("ns_int_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = ns_int, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

```{r, eval = FALSE}
DefaultAssay(ns_int) = "RNA"
setwd("/scratch/groups/khavari/users/andrewji/ns_int/plots")

for (i in 1:length(genes_match))
{
  png(paste("ns_int_",genes_match[i],"_noaxes_nolegend_pt0.25_RNA.png",sep=""), units = "in", height = 5, width = 5, res=300)
  p=FeaturePlot(object = ns_int, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoAxes()
  print(p)
  dev.off()
  png(paste("ns_int_",genes_match[i],"_noaxes_nolegend_pt0.25_RNA_nolegend.png",sep=""), units = "in", height = 5, width = 5, res=300)
  p=FeaturePlot(object = ns_int, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoAxes() + NoLegend()
  print(p)
  dev.off()
}
```
## Save object
```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/")
saveRDS(ns_int, file="ns_int.Rds") 
```
## Find cluster markers
```{r, eval = FALSE}
Idents(ns_int) = "integrated_snn_res.0.4"
setwd("/scratch/groups/khavari/users/andrewji/ns_int/")
markers <- FindAllMarkers(ns_int, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_seurat_markers_res0.4.csv",sep = ",",row.names = T, col.names=T)
```
## remove old objects
```{r, eval = FALSE}
rm(ns_tabib)
rm(ns_cheng)
rm(ns_taka)
rm(all_obj)
rm(ns.list)
```

