---
title: "Creating ns_int_keep"
author: "Larry Chen"
date: "2023-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r load-packages, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
```

```{r Session-Info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

## Load datasets

ns_int_psu_ref contains all confidently identified PSU cells from ns_int. ns_int_fib contains all confidently identified fibroblasts from ns_int.

```{r, eval = FALSE}
ns_int_psu_ref = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_psu_ref.Rds")
DefaultAssay(ns_int_psu_ref) = "RNA"
Idents(ns_int_psu_ref) = "integrated_snn_res.1"

ns_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int.Rds")
DefaultAssay(ns_int) = "RNA"

ns_int_fib = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_fib.Rds")
DefaultAssay(ns_int_fib) = "RNA"
Idents(ns_int_fib) = "integrated_snn_res.0.6"
```

## assigning confident cell IDs

Will be used later for predicting ST spot identities.

### create vector for new celltypes

```{r, eval = FALSE}
ST_celltypes = as.character(ns_int$integrated_snn_res.0.6)
ST_celltypes = paste("res0.6_C",ST_celltypes,sep="")
```

### assigning cell types to PSU cells within ns_int

```{r, eval = FALSE}
psu_celltypes = paste("PSUres1_C",0:17,sep="")
clus = 0:17
#marking PSU cells with their PSU-specific clusters
for (i in 1:length(clus))
{
  cells = WhichCells(ns_int_psu_ref,idents = clus[i])
  ST_celltypes[match(cells,colnames(ns_int))] = psu_celltypes[i]
}
ns_int$ST_celltypes = ST_celltypes
```

### assigning cell types to fibroblasts within ns_int

```{r, eval = FALSE}
#marking fibroblasts with their fibroblast-specific clusters
fib_celltypes = paste("FIBres0.6_C",0:14,sep="")
clus = 0:14
for (i in 1:length(clus))
{
  cells = WhichCells(ns_int_fib,idents = clus[i])
  ST_celltypes[match(cells,colnames(ns_int))] = fib_celltypes[i]
}
ns_int$ST_celltypes = ST_celltypes

dput(unique(ns_int$subcell))
```

### choosing non-fibroblast and PSU cells of interest

```{r, eval = FALSE}
Idents(ns_int) = "subcell"
keep_subcell = c("Bas_I", "Bas_II", "Basal_III", "Cyc_I", "Cyc_II", "Cyc_III", 
                 "Endothelial Cell", "Grn", "LC", 
                 "Melanocyte", "CD1C", "CLEC9A",  "Mac", "MDSC", "Spn_I", "Spn_IFN", "Spn_II", "Spn_III","Tcell")
```

```{r, eval = FALSE}
for (i in 1:length(keep_subcell))
{
  cells = WhichCells(ns_int,idents = keep_subcell[i])
  ST_celltypes[match(cells,colnames(ns_int))] = keep_subcell[i]
  print(paste(keep_subcell[i],length(cells)))
}
ns_int$ST_celltypes = ST_celltypes
dput(names(table(ns_int$ST_celltypes)))
```

## subsetting cells of interest from ns_int

### choosing identities to keep

```{r, eval = FALSE}
keep_celltypes = c("FIBres0.6_C0", "FIBres0.6_C1", "FIBres0.6_C10", "FIBres0.6_C11", 
                   "FIBres0.6_C12", "FIBres0.6_C2", 
                   "FIBres0.6_C3", "FIBres0.6_C4", "FIBres0.6_C5", "FIBres0.6_C6", 
                   "FIBres0.6_C8", "FIBres0.6_C9", "PSUres1_C0", 
                   "PSUres1_C1", "PSUres1_C10", "PSUres1_C11", "PSUres1_C12", "PSUres1_C13", 
                   "PSUres1_C14", "PSUres1_C15", "PSUres1_C16", "PSUres1_C17", "PSUres1_C2", 
                   "PSUres1_C3", "PSUres1_C4", "PSUres1_C5", "PSUres1_C6", "PSUres1_C7", 
                   "PSUres1_C8", "PSUres1_C9",  
                   "res0.6_C16",
                   "res0.6_C21", keep_subcell)
```

### subsetting

```{r, eval = FALSE}
# INTEGRATED predictions

DefaultAssay(ns_int) = "integrated"

Idents(ns_int) = "ST_celltypes"
ns_int_keep = subset(ns_int, idents = keep_celltypes)
```

## save ns_int_keep

```{r, eval = FALSE}
setwd("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int/ns_int_keep")
saveRDS(ns_int_keep,file="ns_int_keep.Rds")
```

## save ns_int_keep metadata

```{r, eval = FALSE}
write.csv(ns_int_keep@meta.data, "C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int/ns_int_keep/ns_int_keep_metadata.csv")
```
