---
title: "Mapping scRNA-seq based cell predictions onto Spatial Transcriptomic data"
author: "Larry Chen"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v4.1.1. You will need to install seurat version 4.1.1 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat4.1.0, eval = FALSE}
remotes::install_version('Seurat', version = '4.1.1', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages/Seurat 4.1.1" )
```

## Import Libraries

```{r, message = FALSE}
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages/Seurat 4.1.1")
library(dplyr)
library(ggplot2)
library(patchwork)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

## Load ST object

```{r}
n23_p1 = readRDS('C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/st/n23_p1.Rds')
```

## Load Predictions

From n23_p1_seurat_prediction_merged_confident_CT_020621.Rmd

```{r}
# Load in ns_int predictions
n23p1_prediction.ns_int = read.table("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/st/n23p1_predictions_ns_int_res0.6_ref.txt",
                              sep = "\t",row.names = 1,header=T,stringsAsFactors = F)

#filter out predictions for spots that were removed
n23_p1_prediction.ns_int_filtered = n23p1_prediction.ns_int[match(colnames(n23_p1),row.names(n23p1_prediction.ns_int)),]
```

```{r}
n23_p1$predicted.id = n23_p1_prediction.ns_int_filtered$predicted.id
Idents(n23_p1) = 'predicted.id'
SpatialDimPlot(n23_p1, images = "rep2")
```

## Feature and Violin Plots

```{r, eval = FALSE}
for (i in 2:42)
{
  id_title = colnames(n23p1_prediction)[i]
  n23_p1@meta.data$pred = as.numeric(n23p1_prediction[,i])
  p = SpatialFeaturePlot(n23_p1,features = "pred")
  png(paste("n23p1_stfeatureplot_",id_title,".png",sep=""),width = 12, height=4, units = "in", res = 300)
  print(p)
  dev.off()
  p2 = VlnPlot(n23_p1,features = "pred",group.by = "SCT_snn_res.0.8")
  pdf(paste("n23p1_vlnplot_res0.8_",id_title,".pdf",sep=""),width = 6, height=4)
  print(p2)
  dev.off()
}
```

```{r, echo = FALSE}
id_title = 'prediction.score.ns_int_res0.6_C2'
n23_p1@meta.data$pred = as.numeric(n23_p1_prediction.ns_int_filtered[,id_title])
print(id_title)
p = SpatialFeaturePlot(n23_p1,features = "pred", images = 'rep2')
print(p + plot_annotation(title = id_title))
```

```{r, echo = FALSE}
id_title = 'prediction.score.ns_int_res0.6_C4'
n23_p1@meta.data$pred = as.numeric(n23_p1_prediction.ns_int_filtered[,id_title])
print(id_title)
p = SpatialFeaturePlot(n23_p1,features = "pred", images = 'rep2')
print(p + plot_annotation(title = id_title))
```

```{r, echo = FALSE}
id_title = 'prediction.score.ns_int_res0.6_C20'
n23_p1@meta.data$pred = as.numeric(n23_p1_prediction.ns_int_filtered[,id_title])
print(id_title)
p = SpatialFeaturePlot(n23_p1,features = "pred", images = 'rep2')
print(p + plot_annotation(title = id_title))
```

## Add IFE/PSU designations to object

IFE/PSU designations made based on histology

```{r, eval = FALSE}
#############
# Check IFE PSU 
# Get IFE/PSU designations and add to each object
n23_p1 = subset(n23_p1, nCount_Spatial > 200)

spot_pos1 = read.table(paste(vis.dir,"IFE_PSU.csv",sep=""),sep = ",",row.names = 1,header = T,stringsAsFactors = F)
spot_pos2 = read.table(paste(vis.dir2,"IFE_PSU.csv",sep=""),sep = ",",row.names = 1,header = T,stringsAsFactors = F)
pos1_names = paste("rep1_",rownames(spot_pos1),sep="")
pos2_names = paste("rep2_",rownames(spot_pos2),sep="")

rownames(spot_pos1) = pos1_names
rownames(spot_pos2) = pos2_names

n23_p1_ifepsu = rep("Other",ncol(n23_p1))
n23_p1_ifepsu_rep1_match = match(rownames(spot_pos1),colnames(n23_p1))
n23_p1_ifepsu_rep1_match_filt = n23_p1_ifepsu_rep1_match[which(!is.na(n23_p1_ifepsu_rep1_match))]
n23_p1_ifepsu[n23_p1_ifepsu_rep1_match_filt] = spot_pos1[,1]
n23_p1_ifepsu_rep2_match = match(rownames(spot_pos2),colnames(n23_p1))
n23_p1_ifepsu_rep2_match_filt = n23_p1_ifepsu_rep2_match[which(!is.na(n23_p1_ifepsu_rep2_match))]
n23_p1_ifepsu[n23_p1_ifepsu_rep2_match_filt] = spot_pos2[,1]

n23_p1$IFE_PSU = n23_p1_ifepsu
```

```{r, eval = FALSE}
Idents(n23_p1) = 'IFE_PSU'
png(paste("n23_p1_IFE_PSU_check.png",sep=""), units = "in", height = 5, width = 10, res=300)
p=SpatialDimPlot(n23_p1)
print(p)
dev.off()
```

```{r, echo = FALSE}
Idents(n23_p1) = 'IFE_PSU'
SpatialDimPlot(n23_p1)
```
