---
title: "Generating celltype predictions for ST spots using scRNA-seq data"
author: "Larry Chen"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v4.1.1. You will need to install seurat version 4.1.1 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat4.1.0, eval = FALSE}
remotes::install_version('Seurat', version = '4.1.1', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages/Seurat 4.1.1" )
```

## Import Libraries

```{r, message = FALSE}
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages/Seurat 4.1.1")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

## Load Data

```{r, eval = FALSE}
ns_int_keep = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int/ns_int_keep/ns_int_keep.Rds")
```

### import ST data

```{r, eval = FALSE}
DefaultAssay(ns_int) = "integrated"
n23_p1 = readRDS("/scratch/groups/khavari/users/andrewji/ST/normal_skin/n23_p1.Rds")
```

## Predictions using ns_int_keep

Make predictions on spot 'cell'-types based on sc-RNAseq data

### N23P1

```{r, eval = FALSE}
n23p1.anchors <- FindTransferAnchors(reference = ns_int_keep, query = n23_p1, 
    dims = 1:30, k.filter=NA)
n23p1_predictions <- TransferData(anchorset = n23p1.anchors, refdata = ns_int_keep$ST_celltypes, 
    dims = 1:30)
```

#### Save predictions as txt

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ST/normal_skin/seurat_pred")
write.table(n23p1_predictions,file="n23p1_predictions_merged_confident_CT.txt",sep="\t",row.names=T,col.names=T)
```

#### Save predictions as txt

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ST/normal_skin/seurat_pred")
write.table(n10_predictions,file="n10_predictions_merged_confident_CT.txt",sep="\t",row.names=T,col.names=T)
```

### Average Expression

```{r, eval = FALSE}
x = AverageExpression(ns_int_keep)
avg_exp_rna = x$RNA
setwd("/scratch/groups/khavari/users/andrewji/ns_int/")
write.table(avg_exp_rna,file="ns_int_keep_celltypes_avg_exp_rna.txt",sep = "\t",row.names = T,col.names = T)
```

```{r, eval = FALSE}
avg_exp_int = x$integrated
write.table(avg_exp_int,file="ns_int_keep_celltypes_avg_exp_int.txt",sep = "\t",row.names = T,col.names = T)
```

## Predictions using ns_int

Used for fig 1

### Load Data

```{r, eval = FALSE}
ns_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int.Rds")
DefaultAssay(ns_int) = "RNA"
```

```{r, eval = FALSE}
ST_celltypes = as.character(ns_int$integrated_snn_res.0.6)
ST_celltypes = paste("ns_int_res0.6_C",ST_celltypes,sep="")
ns_int$ST_celltypes = ST_celltypes
```

### N23P1

```{r, eval = FALSE}
DefaultAssay(ns_int) = "integrated"

n23p1_ns_int.anchors <- FindTransferAnchors(reference = ns_int, query = n23_p1, 
    dims = 1:30, k.filter=NA)
n23p1_ns_int_predictions <- TransferData(anchorset = n23p1_ns_int.anchors, refdata = ns_int$ST_celltypes, 
    dims = 1:30)
```

#### Save predictions as txt

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ST/normal_skin/seurat_pred")
write.table(n23p1_ns_int_predictions,file="n23p1_predictions_ns_int_res0.6_ref.txt",sep="\t",row.names=T,col.names=T)
```

### Average Expression

```{r, eval = FALSE}
x = AverageExpression(ns_int)
avg_exp_rna = x$RNA
setwd("/scratch/groups/khavari/users/andrewji/ns_int/")
write.table(avg_exp_rna,file="ns_int_celltypes_avg_exp_rna.txt",sep = "\t",row.names = T,col.names = T)
```

```{r, eval = FALSE}
avg_exp_int = x$integrated
write.table(avg_exp_int,file="ns_int_celltypes_avg_exp_int.txt",sep = "\t",row.names = T,col.names = T)
```
