---
title: "Creating mu_int/Integrating Mouse Data"
author: "Larry Chen"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package. 
```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
mu_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/mu_int/mu_all_int.Rds")
```

## Read in haensel data

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/haensel_data/analysis/all_merge")

dh_all = c("uw1","uw2","wo1","wo2","wo3")
all_data = list()
for (i in 1:length(dh_all))
{
  data_dir = paste("/oak/stanford/groups/khavari/users/andrewji/mouse_skin/haensel_data/",dh_all[i],sep="")
  list.files(data_dir)
  data = Read10X(data.dir = data_dir)
  #data = Read10X_h5(paste("~/Dropbox/Haensel_Mouse/data/",dh_mouse[i],"_filtered_feature_bc_matrix.h5",sep=""),use.names=TRUE,unique.features = TRUE)
  all_data[[i]] = data
}
```

### Create seurat object from haensel data

```{r, eval = FALSE}
allnames = dh_all
all_obj = list()
for (i in 1:length(all_data))
{
  obj <- CreateSeuratObject(counts = all_data[[i]], project = allnames[i])
  all_obj[[i]] = obj
}
```

### subset by percent.mt \< 10

```{r, eval = FALSE}
dh_all <- merge(all_obj[[1]], y = unlist(all_obj[2:5]), add.cell.ids = allnames, project = "dh_all")

dh_all[["percent.mt"]] <- PercentageFeatureSet(dh_all, pattern = "^mt-")

dh_all = subset(dh_all, percent.mt < 10)
```

## Process joost_main data

### Read In raw data

```{r, eval = FALSE}
joost_main_names = c("5w","9w")

all_data = list()
for (i in 1:length(joost_main_names))
{
  data_dir = paste("/oak/stanford/groups/khavari/users/andrewji/mouse_skin/joost_data/",joost_main_names[i],"_main/",sep="")
  list.files(data_dir)
  data = Read10X(data.dir = data_dir)
  #data = Read10X_h5(paste("~/Dropbox/Haensel_Mouse/data/",dh_mouse[i],"_filtered_feature_bc_matrix.h5",sep=""),use.names=TRUE,unique.features = TRUE)
  all_data[[i]] = data
}
```

### create seurat objects

```{r, eval = FALSE}
allnames = joost_main_names
all_obj = list()
for (i in 1:length(all_data))
{
  obj <- CreateSeuratObject(counts = all_data[[i]], project = allnames[i])
  all_obj[[i]] = obj
}
```

### merge seurat objects

```{r, eval = FALSE}
joost_main <- merge(all_obj[[1]], y = all_obj[[2]], add.cell.ids = allnames, project = "joost_main")
```

## Process joost_val data

### Read In raw data

```{r, eval = FALSE}
joost_val = c("GSM4186888_10X_19_067","GSM4186889_10X_19_069","GSM4186890_10X_19_071",
              "GSM4186891_10X_19_068","GSM4186892_10X_19_070","GSM4186893_10X_19_072")

all_data = list()
for (i in 1:length(joost_val))
{
  #data_dir = paste("/home/andrewji/10x_data/",joost_samples[i],"/outs/filtered_feature_bc_matrix/",sep="")
  #list.files(data_dir)
  #data = Read10X(data.dir = data_dir)
  data = Read10X_h5(paste("~/Dropbox/Joost_Mouse/Joost_2020/data/",joost_val[i],"_filtered_feature_bc_matrix.h5",sep=""),use.names=TRUE,unique.features = TRUE)
  all_data[[i]] = data
}
```

### create seurat objects

```{r, eval = FALSE}
allnames = c("5wk1","5wk2","5wk3","9wk1","9wk2","9wk3")
all_obj = list()
for (i in 1:length(all_data))
{
  obj <- CreateSeuratObject(counts = all_data[[i]], project = allnames[i])
  all_obj[[i]] = obj
}
```

### merge seurat objects

```{r, eval = FALSE}
joost_val <- merge(all_obj[[1]], y = unlist(all_obj[2:6]), add.cell.ids = allnames, project = "joost_val")
```

### save Joost validation seurat object

```{r, eval = FALSE}
setwd("~/Dropbox/Joost_Mouse/Joost_2020/data/")
saveRDS(joost_val,file="mu_skin_val.Rds")
```

## combine Joost validation with Joost Main data

```{r, eval = FALSE}
joost_val = readRDS("/oak/stanford/groups/khavari/users/andrewji/mouse_skin/joost_data/mu_skin_val.Rds")
allnames = c("main","val")
joost_all <- merge(joost_main, y = joost_val, add.cell.ids = allnames, project = "joost_all")
```

### filter out cells by percent.mt \< 10

```{r, eval = FALSE}
joost_all[["percent.mt"]] <- PercentageFeatureSet(joost_all, pattern = "^mt-")

joost_all = subset(joost_all, percent.mt < 10)
```

## Merge Haensel and Joost data

```{r, eval = FALSE}
allnames = c("DH","SJ")
mu_all <- merge(dh_all, y = joost_all, add.cell.ids = allnames, project = "mu_all")
```

## Process full dataset

### normalize/find variable features

```{r, eval = FALSE}
mu.list <- SplitObject(mu_all, split.by = "orig.ident")
# Only non-wounded normal skin
mu.list <- mu.list[c("uw1", "uw2", "5w", "5wk1","5wk2","5wk3","9w","9wk1","9wk2","9wk3")]
for (i in 1:length(mu.list)) {
    mu.list[[i]] <- NormalizeData(mu.list[[i]], verbose = FALSE)
    mu.list[[i]] <- FindVariableFeatures(mu.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

### Integrate

```{r, eval = FALSE}
reference.list <- mu.list
mu.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

mu_int <- IntegrateData(anchorset = mu.anchors, dims = 1:30)
DefaultAssay(mu_int) <- "integrated"
```

### Scale/PCA/UMAP

```{r, eval = FALSE}
mu_int <- ScaleData(mu_int, verbose = FALSE)
mu_int <- RunPCA(mu_int, npcs = 30, verbose = FALSE)
mu_int <- RunUMAP(mu_int, reduction = "pca", dims = 1:30)
```

### Clustering

```{r, eval = FALSE}
mu_int <- FindNeighbors(mu_int, dims = 1:30, verbose = T)
mu_int <- FindClusters(mu_int, resolution = 0.1, verbose = FALSE)
#mu_int <- FindClusters(mu_int, resolution = 0.15, verbose = FALSE)
mu_int <- FindClusters(mu_int, resolution = 0.2, verbose = FALSE)
#mu_int <- FindClusters(mu_int, resolution = 0.25, verbose = FALSE)
#mu_int <- FindClusters(mu_int, resolution = 0.3, verbose = FALSE)
mu_int <- FindClusters(mu_int, resolution = 0.4, verbose = FALSE)
mu_int <- FindClusters(mu_int, resolution = 0.6, verbose = FALSE)
mu_int <- FindClusters(mu_int, resolution = 0.8, verbose = FALSE)
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/")
saveRDS(mu_int, file="mu_all_int.Rds") 
```

## assign labels to samples

```{r, eval = FALSE}
# Label by Anagen and Telogen
Idents(mu_int) = "orig.ident"
dput(levels(Idents(mu_int)))
clus = c("uw1", "uw2", "5w", "5wk1", "5wk2", "5wk3", 
"9w", "9wk1", "9wk2","9wk3")
clus_names = c(rep("DH",2),rep("SJ",8))
clus_names2 = c(rep("NA",2),"Main","Val","Val","Val","Main","Val","Val","Val")
tel_ana_names = c(rep("NA",2),rep("ANA",4),rep("TEL",4))
dataset = rep("x",ncol(mu_int))
tel_ana = rep("x",ncol(mu_int))
main_val = rep("x",ncol(mu_int))
for (i in 1:length(clus))
{
  cells = WhichCells(mu_int, idents = clus[i])
  dataset[match(cells,colnames(mu_int))] = clus_names[i]
  main_val[match(cells,colnames(mu_int))] = clus_names2[i]
  tel_ana[match(cells,colnames(mu_int))] = tel_ana_names[i]
}
```

```{r, eval = FALSE}
mu_int$dataset = dataset

mu_int$hf_cycle = tel_ana
mu_int$main_val = main_val
```

## Graphing

### UMAPS

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/plots")

png("mu_int_labelbysample.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int, reduction = "umap", group.by = "orig.ident")
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int, reduction = "umap", group.by = "orig.ident")
```

```{r, eval = FALSE}
png("mu_int_groupby_dataset.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int, reduction="umap", label=T, group.by = "dataset", pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int, reduction="umap", label=T, group.by = "dataset", pt.size = 0.1)
```

```{r, eval = FALSE}
png("mu_int_groupby_mainval.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int, reduction="umap", label=T, group.by = "main_val", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int, reduction="umap", label=T, group.by = "main_val", pt.size = 0.25)
```

```{r, eval = FALSE}
png("mu_int_groupby_hfcycle.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int, reduction="umap", label=T, group.by = "hf_cycle", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int, reduction="umap", label=T, group.by = "hf_cycle", pt.size = 0.25)
```

#### UMAPS colored by cluster resolutions

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(mu_int) = paste("integrated_snn_res.",res,sep="")
  png(paste("mu_int_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(mu_int, reduction="umap", label=T, do.return = T, pt.size = 0.1)
  print(p)
  dev.off()
}
```

### Feature Plots

```{r, eval = FALSE}
genes = c("Krt14", "Krt5", "Krt1", "Krt10", "Lhx2", "Krt19", 
"Azgp1", "Krt15", "Sox9", "Cd14", "Cd207", "Cd3e", "Mlana", "Vwf", 
"Col1a1", "S100a8", "S100a9", "Clec9a", "Mgst1", "Apoe", 
"Xcl1", "Mki67", "Ccr7", "Ccl19", "Sele", "Dio2", "Wif1", "Krt15", 
"Col17a1", "Flg", "Cd34", "Itga6", "Col17a1", "Itgb1", "Itgb4", 
"Barx2", "Msx2", "Krt25", "Krt27", "Krt71", "Krt79", "Pthlh", 
"Lgr5", "Lgr6", "Cst6", "Fgf5", "Krt31", "Sparc", "Dcn", "Corin", 
"Sfrp1", "Edn2", "Tagln","Des","Myh9","Krt35","Acta1",
"Ptn","Sostdc1","Dkk3","Tnc","Sfrp2","Lamb3", "Itgam","Itgax","Ptn","Sostdc1",
"Fcgbp","H2-M2","Epgn","Ivl","H2-Aa","Cd74","S100a1","Them5","Calml3",
"Sbsn","Dmkn","Nog","Tspan2","Grem1","Aqp5","Fgf18","Il11ra1",
"Il31ra","Mfap2","Cldn10","Fam13a","Mt1","Mt2","Mmp10","Pthlh","Tnc","Mdk","Lgals1")
#genes = "MT-CYB"

genes_match = genes[genes %in% rownames(mu_int)]

for (i in 1:length(genes_match))
{
  png(paste("mu_int_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = mu_int, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Find All Markers

```{r, eval = FALSE}
Idents(mu_int) = "integrated_snn_res.0.4"
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/")
markers <- FindAllMarkers(mu_int, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "mu_int_seurat_markers_res0.4.csv",sep = ",",row.names = T, col.names=T)
```
