---
title: "Isolating Mouse Mesenchymal cells"
author: "Larry Chen"
date: "2023-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

## Import Libraries

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
mu_int_fib = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/mu_int/mes/mu_int_fib.Rds")
```

## Load Object

```{r, eval = FALSE}
mu_int = readRDS("/oak/stanford/groups/khavari/users/andrewji/seurat_obj/mu_all_int.Rds") 
```

## Subset mesenchymal cells/fibroblasts

```{r, eval = FALSE}
Idents(mu_int) = "integrated_snn_res.0.6"
mu_int_fib = subset(mu_int, idents = c(6,8,16,28))
```

## Preprocess data/select samples

non-wounded normal skin

```{r, eval = FALSE}
mu.list <- SplitObject(mu_int_fib, split.by = "orig.ident")


# Only non-wounded normal skin
mu.list <- mu.list[c("uw1", "uw2", "5w", "5wk1","5wk2","5wk3","9w","9wk1","9wk2","9wk3")]
for (i in 1:length(mu.list)) {
    mu.list[[i]] <- NormalizeData(mu.list[[i]], verbose = FALSE)
    mu.list[[i]] <- FindVariableFeatures(mu.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

## Integrate

```{r, eval = FALSE}
reference.list <- mu.list
mu.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30, k.filter = 105)

mu_int_fib <- IntegrateData(anchorset = mu.anchors, dims = 1:30)
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
DefaultAssay(mu_int_fib) <- "integrated"
mu_int_fib <- ScaleData(mu_int_fib, verbose = FALSE)
mu_int_fib <- RunPCA(mu_int_fib, npcs = 30, verbose = FALSE)
mu_int_fib <- RunUMAP(mu_int_fib, reduction = "pca", dims = 1:30)
```

## Clustering

```{r, eval = FALSE}
mu_int_fib <- FindNeighbors(mu_int_fib, dims = 1:30, verbose = T)
mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.1, verbose = FALSE)
#mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.15, verbose = FALSE)
mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.2, verbose = FALSE)
#mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.25, verbose = FALSE)
#mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.3, verbose = FALSE)
mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.4, verbose = FALSE)
mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.6, verbose = FALSE)
mu_int_fib <- FindClusters(mu_int_fib, resolution = 0.8, verbose = FALSE)
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_fib/")
saveRDS(mu_int_fib, file="mu_int_fib.Rds") 
```

## Label by Anagen and Telogen

```{r, eval = FALSE}
# Label by Anagen and Telogen
Idents(mu_int_fib) = "orig.ident"
dput(levels(Idents(mu_int_fib)))
clus = c("uw1", "uw2", "5w", "5wk1", "5wk2", "5wk3", 
"9w", "9wk1", "9wk2","9wk3")
clus_names = c(rep("DH",2),rep("SJ",8))
clus_names2 = c(rep("NA",2),"Main","Val","Val","Val","Main","Val","Val","Val")
tel_ana_names = c(rep("NA",2),rep("ANA",4),rep("TEL",4))
dataset = rep("x",ncol(mu_int_fib))
tel_ana = rep("x",ncol(mu_int_fib))
main_val = rep("x",ncol(mu_int_fib))
for (i in 1:length(clus))
{
  cells = WhichCells(mu_int_fib, idents = clus[i])
  dataset[match(cells,colnames(mu_int_fib))] = clus_names[i]
  main_val[match(cells,colnames(mu_int_fib))] = clus_names2[i]
  tel_ana[match(cells,colnames(mu_int_fib))] = tel_ana_names[i]
}
mu_int_fib$dataset = dataset

mu_int_fib$hf_cycle = tel_ana
mu_int_fib$main_val = main_val
```

## UMAPS

### By sample

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_fib/plots")
png("mu_int_fib_labelbysample.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int_fib, reduction = "umap", group.by = "orig.ident")
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_fib, reduction = "umap", group.by = "orig.ident")
```

### By dataset

```{r, eval = FALSE}
png("mu_int_fib_groupby_dataset.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "dataset", pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "dataset", pt.size = 0.1)
```

### By main_val

Sample is from Joost Main or Joost Validation

```{r, eval = FALSE}
png("mu_int_fib_groupby_mainval.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "main_val", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "main_val", pt.size = 0.25)
```

### By hf_cycle

```{r, eval = FALSE}
png("mu_int_fib_groupby_hfcycle.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "hf_cycle", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_fib, reduction="umap", label=T, group.by = "hf_cycle", pt.size = 0.25)
```

### By cluster

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(mu_int_fib) = paste("integrated_snn_res.",res,sep="")
  png(paste("mu_int_fib_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(mu_int_fib, reduction="umap", label=T, do.return = T, pt.size = 0.1)
  print(p)
  dev.off()
}
```

```{r, echo = FALSE}
Idents(mu_int_fib) = "integrated_snn_res.0.6"
DimPlot(mu_int_fib, reduction="umap", label=T, do.return = T, pt.size = 0.1)
```

## Feature Plots

```{r, eval = FALSE}
DefaultAssay(mu_int_fib) = "RNA"
genes = c("Krt14", "Krt5", "Krt1", "Krt10", "Lhx2", "Krt19", 
"Azgp1", "Krt15", "Col1a1","Thy1","Pdgfra","Pdgfrb","Acta2","Mcam","Myh9","Sparc","Lum",
"Il31ra","Mfap2","Cldn10","Fam13a","Mt1","Mt2","Mmp10","Pthlh","Tnc","Mdk","Lgals1",
"Cxcl12","Gpx3","Mfap5","Corin","Dcn","Tagln","Des","Acta1","Sfrp2","Cd34",
"Tnn","Abi3bp","Ramp1","Crabp1","Notum","Pappa2","Nrg2","Cntn1","Grem2","Mylk",
"Acan","Sox2","Lef1","Ccl2","Cd276","Mki67","Top2a")
#genes = "MT-CYB"
genes_match = genes[genes %in% rownames(mu_int_fib)]

for (i in 1:length(genes_match))
{
  png(paste("mu_int_fib_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = mu_int_fib, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Find Markers

```{r, eval = FALSE}
Idents(mu_int_fib) = "integrated_snn_res.0.6"
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_fib")
markers <- FindAllMarkers(mu_int_fib, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "mu_int_fib_seurat_markers_res0.6.csv",sep = ",",row.names = T, col.names=T)
```
