---
title: "Isolating human mesenchymal/fibroblast cells"
author: "Larry Chen"
date: "2023-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

## Import Libraries

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
ns_int_fib = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_fib.Rds")
```
## load object
```{r, eval = FALSE}
ns_int = readRDS("/scratch/groups/khavari/users/andrewji/ns_int/ns_int.Rds")
DefaultAssay(ns_int) = "RNA"
```

## Subset mesenchymal cells
```{r, eval = FALSE}
res = 0.6
Idents(ns_int) = paste("integrated_snn_res.",res,sep="")
ns_int_fib = subset(ns_int, idents = 6)
#saveRDS(ns_int_fib, file="ns_int_fib.Rds")
```

##Adding in fibroblasts that clustered with PSU cells
We first import the PSU cell dataset.
```{r, eval = FALSE}
ns_int_psu_noecc = readRDS("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu_noecc/ns_int_psu_noecc.Rds")
DefaultAssay(ns_int_psu_noecc) = "RNA"
```
We then select cluster 5 at RNA resolution 0.6, which represents the fibroblasts.
```{r, eval = FALSE}
Idents(ns_int_psu_noecc) = "RNA_snn_res.0.6"
# Filter out cluster 5, which are fibroblasts
ns_int_psu_fib = subset(ns_int_psu_noecc, idents = 5)
```
Finally, we merge the errant cluster with the rest of the mesenchymal cells. 
```{r, eval = FALSE}
ns_int_fib = merge(ns_int_fib, ns_int_psu_fib)
```

## Split object
We only selected samples that had more than 100 cells.
```{r, eval = FALSE}
ns.list <- SplitObject(ns_int_fib, split.by = "sample")

x=which(table(ns_int_fib$sample)>100)
# sample_keep = c("abd4", "br41epi", "br53epi", "P1", "P10", "P2", "P5", "P6", 
# "P7", "P9", "rt1", "s11", "SC18control", "SC34control", "scalp26", 
# "scalp32")
sample_keep = names(x)
ns.list = ns.list[sample_keep]
```

## Preprocessing
```{r, eval = FALSE}
for (i in 1:length(ns.list)) {
    ns.list[[i]] <- NormalizeData(ns.list[[i]], verbose = FALSE)
    ns.list[[i]] <- FindVariableFeatures(ns.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```
```{r, eval = FALSE}
reference.list <- ns.list
ns.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30, k.filter = 100)

ns_int_fib <- IntegrateData(anchorset = ns.anchors, dims = 1:30)
```

## Scale/PCA/UMAP
```{r, eval = FALSE}
DefaultAssay(ns_int_fib) <- "integrated"
ns_int_fib <- ScaleData(ns_int_fib, verbose = FALSE)
ns_int_fib <- RunPCA(ns_int_fib, npcs = 30, verbose = FALSE)
ns_int_fib <- RunUMAP(ns_int_fib, reduction = "pca", dims = 1:30)
```


## Clustering 
```{r, eval = FALSE}
ns_int_fib <- FindNeighbors(ns_int_fib, dims = 1:30, verbose = T)
ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.1, verbose = FALSE)
#ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.15, verbose = FALSE)
ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.2, verbose = FALSE)
#ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.25, verbose = FALSE)
#ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.3, verbose = FALSE)
ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.4, verbose = FALSE)
ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.6, verbose = FALSE)
ns_int_fib <- FindClusters(ns_int_fib, resolution = 0.8, verbose = FALSE)
```

## Save Object
```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_fib")
saveRDS(ns_int_fib, file="ns_int_fib.Rds") 
```

## UMAPS
### By sample
```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_fib/plots")
png("ns_int_fib_labelby_sample.png", units = "in", height = 5, width = 8, res=300)
DimPlot(ns_int_fib, reduction = "umap", group.by = "sample")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_fib, reduction = "umap", group.by = "sample")
```

### By dataset
```{r, eval = FALSE}
png("ns_int_fib_labelby_dataset.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_fib, reduction = "umap", group.by = "dataset")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_fib, reduction = "umap", group.by = "dataset")
```

### By subcell
```{r, eval = FALSE}
png("ns_int_fib_labelby_subcell.png", units = "in", height = 5, width = 8, res=300)
DimPlot(ns_int_fib, reduction = "umap", group.by = "subcell")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_fib, reduction = "umap", group.by = "subcell")
```

### By percent.mt
```{r, eval = FALSE}
png("ns_int_fib_labelby_percentmt.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_fib, features = "percent.mt")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_fib, features = "percent.mt")
```

### by nCount_RNA
```{r, eval = FALSE}
png("ns_int_fib_labelby_nUMI.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_fib, features = "nCount_RNA")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_fib, features = "nCount_RNA")
```

### by nFeature_RNA
```{r, eval = FALSE}
png("ns_int_fib_labelby_nFeature.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_fib, features = "nFeature_RNA")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_fib, features = "nFeature_RNA")
```

### by clusters
```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(ns_int_fib) = paste("integrated_snn_res.",res,sep="")
  png(paste("ns_int_fib_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(ns_int_fib, reduction="umap", label=T, do.return = T, pt.size = 0.1)
  print(p)
  dev.off()
}
```

```{r, echo = FALSE}
Idents(ns_int_fib) = "integrated_snn_res.0.6"
DimPlot(ns_int_fib, reduction="umap", label=T, do.return = T, pt.size = 0.1)
```

## Feature Plots
```{r, eval = FALSE}
genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207",
	"CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1",
	"KRT23","KRT25","KRT6A","KRT16","KRT17","PPARG","DIO2","COMP","FGF7","COL17A1","TP63","PTN","SAT1","SOX4","KLF5","TNC",
	"PTHLH","MT1X","MT1G","MT1H","MT1E","SFRP1","DMKN","ZNF750","IVL","SOSTDC1","FGF18","IL37","IL1F10","IL36RN","IL1RN",
	"MDK","LGALS1","CD151","ITGB1","MKI67","LUM","COL6A1","SOX2","DHRS9","LCE1E","PIP",
	"CORIN","NOG","FGF10","BMP2","BMP4","BMP7","MCAM","ACTA2","DES","MYH9","CCDC80","DPP4","SPARC","LUM","SFRP2","FMO1",
	"LSP1","CRABP1","COL11A1")

#genes = "MT-CYB"
DefaultAssay(ns_int_fib) = "RNA"
genes_match = genes[genes %in% rownames(ns_int_fib)]

for (i in 1:length(genes_match))
{
  png(paste("ns_int_fib_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = ns_int_fib, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Find Markers
```{r, eval = FALSE}
Idents(ns_int_fib) = "integrated_snn_res.0.6"
markers <- FindAllMarkers(ns_int_fib, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_fib_seurat_markers_res0.6.csv",sep = ",",row.names = T, col.names=T)
```