---
title: "Filtering mouse IFE cells"
author: "Larry Chen"
date: "2023-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
mu_int_ife_filt = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/mu_int/mu_int_ife_filt.Rds")
```

## Load Object

```{r, eval = FALSE}
mu_int_ife = readRDS("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife.Rds") 
Idents(mu_int_ife) = "integrated_snn_res.0.6"
```

## Subset Object to remove contaminating non IFE cells

```{r, eval = FALSE}
mu_int_ife_filt = subset(mu_int_ife, idents = c(0,1,3,4,5,6,9,10,11,12,15)) # exclude 2,7,8,13,14
DefaultAssay(mu_int_ife_filt) = "RNA"
dim(mu_int_ife_filt)
```

## Preprocessing

```{r, eval = FALSE}
mu.list <- SplitObject(mu_int_ife_filt, split.by = "orig.ident")

# Only non-wounded normal skin
#mu.list <- mu.list[c("uw1", "uw2", "5w", "5wk1","5wk2","5wk3","9w","9wk1","9wk2")]
for (i in 1:length(mu.list)) {
    mu.list[[i]] <- NormalizeData(mu.list[[i]], verbose = FALSE)
    mu.list[[i]] <- FindVariableFeatures(mu.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
    print(i)
}
```

## Integrate

```{r, eval = FALSE}
reference.list <- mu.list
mu.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

mu_int_ife_filt <- IntegrateData(anchorset = mu.anchors, dims = 1:30)
print(dim(mu_int_ife_filt))
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
DefaultAssay(mu_int_ife_filt) <- "integrated"
mu_int_ife_filt <- ScaleData(mu_int_ife_filt, verbose = FALSE)
mu_int_ife_filt <- RunPCA(mu_int_ife_filt, npcs = 30, verbose = FALSE)
mu_int_ife_filt <- RunUMAP(mu_int_ife_filt, reduction = "pca", dims = 1:30)
```

## DimPlot by sample

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt/plots")

png("mu_int_ife_filt_labelbysample.png", units = "in", height = 5, width = 6, res=300)
p1 <- DimPlot(mu_int_ife_filt, reduction = "umap", group.by = "orig.ident")
print(p1)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_ife_filt, reduction = "umap", group.by = "orig.ident")
```

## Add Joost annotations

```{r, eval = FALSE}
# Add Joost annotations
mu_int_metadata = read.table("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_metadata.txt",sep="\t",
  row.names=1,header=T,stringsAsFactors = F)
mu_int_ife_filt$sj_anno_nomu = mu_int_metadata[colnames(mu_int_ife_filt),"sj_anno_nomu"]
```

```{r, eval = FALSE}
png("mu_int_ife_filt_labelby_sj_anno_nomu.png", units = "in", height = 5, width = 6, res=300)
p1 <- DimPlot(mu_int_ife_filt, reduction = "umap", group.by = "sj_anno_nomu")
print(p1)
dev.off()
png("mu_int_ife_filt_labelby_sj_anno_nomu_label.png", units = "in", height = 5, width = 6, res=300)
p1 <- DimPlot(mu_int_ife_filt, label=T, reduction = "umap", group.by = "sj_anno_nomu")
print(p1)
dev.off()
```

## Clustering

```{r, eval = FALSE}
mu_int_ife_filt <- FindNeighbors(mu_int_ife_filt, dims = 1:30, verbose = T)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.1, verbose = FALSE)
#mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.15, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.2, verbose = FALSE)
#mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.25, verbose = FALSE)
#mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.3, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.4, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.6, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 0.8, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 1, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 1.2, verbose = FALSE)
mu_int_ife_filt <- FindClusters(mu_int_ife_filt, resolution = 1.5, verbose = FALSE)
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt")
saveRDS(mu_int_ife_filt, file="mu_int_ife_filt.Rds") 
```

## Graphing

### UMAPs

#### By Sample

```{r, eval = FALSE}
png("mu_int_ife_filt_labelby_sample.png", units = "in", height = 5, width = 6, res=300)
DimPlot(mu_int_ife_filt, reduction="umap", do.label=F, group.by = "orig.ident", do.return = T, pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_ife_filt, reduction="umap", label = F, group.by = "orig.ident", pt.size = 0.25)
```

#### By clusters (\@ diff res)

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8,1,1.2,1.5)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(mu_int_ife_filt) = paste("integrated_snn_res.",res,sep="")
  png(paste("mu_int_ife_filt_res_",res,".png",sep=""), units = "in", height = 5, width = 6, res=300)
  p=DimPlot(mu_int_ife_filt, reduction="umap", label=T, do.return = T, pt.size = 0.25)
  print(p)
  dev.off()
}
```

```{r, echo = FALSE}
Idents(mu_int_ife_filt) = 'integrated_snn_res.0.4'
DimPlot(mu_int_ife_filt, reduction="umap", label=T, pt.size = 0.25)
```

#### By NCountRNA

```{r, eval = FALSE}
png("mu_int_ife_filt_nUMI.png", units = "in", height = 5, width = 5.5, res=300)
p=FeaturePlot(object = mu_int_ife_filt, features = "nCount_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
p = p + NoAxes()
print(p)
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(object = mu_int_ife_filt, features = "nCount_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
```

#### By nFeature_RNA

```{r, eval = FALSE}
png("mu_int_ife_filt_nFeature.png", units = "in", height = 5, width = 5.5, res=300)
p=FeaturePlot(object = mu_int_ife_filt, features = "nFeature_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
p = p + NoAxes()
print(p)
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(object = mu_int_ife_filt, features = "nFeature_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
```

## Feature Plots

```{r, eval = FALSE}
DefaultAssay(mu_int_ife_filt) = "RNA"

genes = c("Krt14", "Krt5", "Krt1", "Krt10", "Lhx2", "Krt19", 
"Azgp1", "Krt15", "Sox9", "Cd14", "Cd207", "Cd3e", "Mlana", "Vwf", 
"Col1a1", "S100a8", "S100a9", "Clec9a", "Mgst1", "Apoe", 
"Xcl1", "Mki67", "Ccr7", "Ccl19", "Sele", "Dio2", "Wif1", "Krt15", 
"Col17a1", "Flg", "Lor","Cd34", "Itga6", "Col17a1", "Itgb1", "Itgb4", 
"Barx2", "Msx2", "Krt25", "Krt27", "Krt71", "Krt79", "Pthlh", 
"Lgr5", "Lgr6", "Cst6", "Fgf5", "Krt31", 
"Sfrp1", "Edn2", "Tagln",
"Ptn","Sostdc1","Dkk3","Tnc","Sfrp2","Lamb3","Trp63","Klk7","Ivl","Lce1a1")

genes_match = genes[genes %in% rownames(mu_int_ife_filt)]
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt/plots")

genes = c("Col17a1","Mki67","Klk7","Krt10","Itga6","Krt1","Zfp750","Ivl","Itgb4","Itgb1")
genes_match = genes[genes %in% rownames(mu_int_ife_filt)]
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt/plots")
```

```{r, eval = FALSE}
for (i in 1:length(genes_match))
{
  png(paste("mu_int_ife_filt_",genes_match[i],"_noaxes_nolegend_pt1_RNA_nolegend.png",sep=""), units = "in", height = 5, width = 5, res=300)
  p=FeaturePlot(object = mu_int_ife_filt, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 1, order=T)
  p = p + NoAxes() + NoLegend()
  print(p)
  dev.off()
}
```

```{r, eval = FALSE}
png("mu_int_ife_filt_labelby_ccphase_2d.png", units = "in", height = 5, width = 6, res=300)
p1 <- DimPlot(mu_int_ife_filt, reduction = "umap", group.by = "Phase")
print(p1)
dev.off()
```

```{r, echo = FALSE}
DimPlot(mu_int_ife_filt, reduction = "umap", group.by = "Phase")
```

```{r, eval = FALSE}
genes_match = c("S.Score","G2M.Score")
for (i in 1:length(genes_match))
{
  png(paste("mu_int_ife_filt_",genes_match[i],"_noaxes_nolegend_pt0.25_RNA.png",sep=""), units = "in", height = 5, width = 5, res=300)
  p=FeaturePlot(object = mu_int_ife_filt, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoAxes()
  print(p)
  dev.off()
}
```

## Cell Cycle Scoring

```{r, eval = FALSE}
# Cell cycle scoring
DefaultAssay(mu_int_ife_filt) = "RNA"

mu_cc_genes = readRDS("/scratch/groups/khavari/users/andrewji/mu_all/mouse_cell_cycle_genes.rds")

s.genes <- mu_cc_genes$s.genes
g2m.genes <- mu_cc_genes$g2m.genes
mu_int_ife_filt <- CellCycleScoring(mu_int_ife_filt, s.features = s.genes, g2m.features = g2m.genes, set.ident = TRUE)
```

### UMAP by Cell Cycle Scores

```{r, eval = FALSE}
cols = c("palevioletred","goldenrod","turquoise3")
Idents(mu_int_ife_filt) = "Phase"
p = DimPlot(mu_int_ife_filt, pt.size = 0.25, cols = cols)
p = p + NoLegend() + NoAxes()
png("mu_int_ife_filt_cc_phase_newcols_nolegend.png", units = "in", height = 5, width = 5, res=300)
print(p)
dev.off()
```

## Find all markers

```{r, eval = FALSE}
Idents(mu_int_ife_filt) = "integrated_snn_res.0.4"
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt")
markers <- FindAllMarkers(mu_int_ife_filt, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "mu_int_ife_filt_seurat_markers_res0.4.csv",sep = ",",row.names = T, col.names=T)
```

## Save Metadata

```{r, eval = FALSE}
mu_int_ife_filt_metadata = as.matrix(mu_int_ife_filt@meta.data)
write.table(mu_int_ife_filt_metadata,file="mu_int_ife_filt_metadata.txt",sep="\t",col.names=T,row.names=T)
```

### extra graphs

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt/plots")

res = 0.4
Idents(mu_int_ife_filt) = "integrated_snn_res.0.4"
png(paste("mu_int_ife_filt_res_",res,"_nolabel.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=F, pt.size = 0.25)
print(p)
dev.off()
png(paste("mu_int_ife_filt_res_",res,"_color_order.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=T, pt.size = 0.25)
print(p)
dev.off()
png(paste("mu_int_ife_filt_res_",res,"_nolabel_color_order.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=F, pt.size = 0.25)
print(p)
dev.off()
png(paste("mu_int_ife_filt_res_",res,"_noaxes_color_order.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=T, pt.size = 0.25)
p = p+NoAxes()
print(p)
dev.off()
png(paste("mu_int_ife_filt_res_",res,"_noaxes_nolabel_color_order.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=F, pt.size = 0.25)
p = p+NoAxes()
print(p)
dev.off()
png(paste("mu_int_ife_filt_res_",res,"_noaxes_color_order_largelabel.png",sep=""), units = "in", height = 5, width = 6, res=300)
p=DimPlot(mu_int_ife_filt, reduction="umap", label=T,label.size = 8, pt.size = 0.25)
p = p+NoAxes()
print(p)
dev.off()
```

## Dot Plots

```{r, include = FALSE}
Idents(mu_int_ife_filt) = "integrated_snn_res.0.4"
markers <- FindAllMarkers(mu_int_ife_filt, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
mu_ife_markers = subset(markers, p_val_adj < 0.05)
mu_ife_markers_top10 = mu_ife_markers %>% group_by(cluster) %>% top_n(10, avg_logFC) 
```

```{r, eval = FALSE}
###
# Dot plots

mu_ife_markers = read.table("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/mu_int_ife_filt/mu_int_ife_filt_seurat_markers_res0.4.csv", sep=",",stringsAsFactors=F,header=T,row.names=1)                   
mu_ife_markers_top10 = mu_ife_markers %>% group_by(cluster) %>% top_n(10, avg_logFC) 
```

```{r}
mu_top10_unique = unique(mu_ife_markers_top10$gene)
order_clus = c(0,1,4,9,5,7,6,2,3,8)
mu_top10_reorder = mu_top10_unique[c(1:20,38:47,78:86,48:57,68:74,58:67,21:37,75:77)]
Idents(mu_int_ife_filt) = "integrated_snn_res.0.4"
Idents(mu_int_ife_filt) = factor(x = Idents(mu_int_ife_filt), levels = order_clus)
```

```{r, eval = FALSE}
library(ggplot2)
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_ordered_vert.pdf",height = 7, width = 16,useDingbats=F)
p = DotPlot(mu_int_ife_filt, features = rev(mu_top10_reorder))
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_ordered.pdf",height = 5, width = 16,useDingbats=F)
p = DotPlot(mu_int_ife_filt, features = mu_top10_reorder)
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
Idents(mu_int_ife_filt) = factor(x = Idents(mu_int_ife_filt), levels = rev(order_clus))
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_rev_ordered.pdf",height = 5, width = 16,useDingbats=F)
p = DotPlot(mu_int_ife_filt, features = rev(mu_top10_reorder))
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()

pdf("mu_int_ife_filt_res_0.4_marker_dotplot_ordered.pdf",height = 5, width = 16,useDingbats=F)
p = DotPlot(mu_int_ife_filt, features = mu_top10_reorder)
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_ordered_rtaxis.pdf",height = 5, width = 16,useDingbats=F)
p = DotPlot(mu_int_ife_filt, features = mu_top10_reorder)
p = p + RotatedAxis()
print(p)
dev.off()

pdf("mu_int_ife_filt_res_0.4_marker_dotplot.pdf",height = 5, width = 16)
p = DotPlot(mu_int_ife_filt, features = mu_top10_unique)
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_rtaxis.pdf",height = 5, width = 16)
p = DotPlot(mu_int_ife_filt, features = mu_top10_unique)
p = p + RotatedAxis()
print(p)
dev.off()

```

```{r, eval = FALSE}
mu_int_ife_filt_sub = subset(mu_int_ife_filt,idents = c(0:6,8:12))
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_subset.pdf",height = 5, width = 19, useDingbats=F)
p = DotPlot(mu_int_ife_filt_sub, features = rev(mu_top10_unique[c(1:67,78:121)]))
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_subset_45.pdf",height = 4, width = 22,  useDingbats=F)
p = DotPlot(mu_int_ife_filt_sub, features = rev(mu_top10_unique[c(1:67,78:121)])) + RotatedAxis()
print(p)
dev.off()

pdf("mu_int_ife_filt_res_0.4_marker_dotplot_subset_Rdbu.pdf",height = 5, width = 19,  useDingbats=F)
p = DotPlot(mu_int_ife_filt_sub, features = rev(mu_top10_unique[c(1:67,78:121)]), cols = "RdBu")
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
dev.off()
pdf("mu_int_ife_filt_res_0.4_marker_dotplot_subset_45_Rdbu.pdf",height = 4, width = 22,  useDingbats=F)
p = DotPlot(mu_int_ife_filt_sub, features = rev(mu_top10_unique[c(1:67,78:121)]),  cols = "RdBu") + RotatedAxis()
print(p)
dev.off()
```

```{r, echo = FALSE}
p = DotPlot(mu_int_ife_filt, features = mu_top10_reorder)
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p
```
