---
title: "Isolating mouse IFE cells"
author: "Larry Chen"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package. 
```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```
## Import object
```{r}
mu_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/mu_int/mu_all_int.Rds") 
```
## Subset Object by IFE cells
```{r}
Idents(mu_int) = "integrated_snn_res.0.6"
mu_int_ife = subset(mu_int, idents = c(0,3,4,9,12,2,22))
DefaultAssay(mu_int_ife) = "RNA"
```

## Preprocessing
```{r}
mu.list <- SplitObject(mu_int_ife, split.by = "orig.ident")

# Only non-wounded normal skin
#mu.list <- mu.list[c("uw1", "uw2", "5w", "5wk1","5wk2","5wk3","9w","9wk1","9wk2")]
for (i in 1:length(mu.list)) {
    mu.list[[i]] <- NormalizeData(mu.list[[i]], verbose = FALSE)
    mu.list[[i]] <- FindVariableFeatures(mu.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
    print(i)
}
```
## Integrate
```{r,  message = FALSE}
reference.list <- mu.list
mu.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

mu_int_ife <- IntegrateData(anchorset = mu.anchors, dims = 1:30)
print(dim(mu_int_ife))
```
## Scale/PCA/UMAP
```{r}
DefaultAssay(mu_int_ife) <- "integrated"
mu_int_ife <- ScaleData(mu_int_ife, verbose = FALSE)
mu_int_ife <- RunPCA(mu_int_ife, npcs = 30, verbose = FALSE)
mu_int_ife <- RunUMAP(mu_int_ife, reduction = "pca", dims = 1:30)
```

## UMAPS
```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/plots")

png("mu_int_ife_labelbysample.png", units = "in", height = 5, width = 6, res=300)
p1 <- DimPlot(mu_int_ife, reduction = "umap", group.by = "orig.ident")
print(p1)
dev.off()
```

## mu_int_ife
```{r, echo = FALSE}
DimPlot(mu_int_ife, reduction = "umap", group.by = "orig.ident")
```

```{r, eval = FALSE}
png("mu_int_ife_labelby_sj_anno_nomu.png", units = "in", height = 5, width = 8, res=300)
p1 <- DimPlot(mu_int_ife, reduction = "umap", group.by = "sj_anno_nomu")
print(p1)
dev.off()
```


```{r, eval = FALSE}
png("mu_int_ife_labelby_sj_anno_nomu_label.png", units = "in", height = 5, width = 8, res=300)
p1 <- DimPlot(mu_int_ife, label=T, reduction = "umap", group.by = "sj_anno_nomu")
print(p1)
dev.off()
```

## Clustering
```{r, eval = FALSE}
mu_int_ife <- FindNeighbors(mu_int_ife, dims = 1:30, verbose = T)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.1, verbose = FALSE)
#mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.15, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.2, verbose = FALSE)
#mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.25, verbose = FALSE)
#mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.3, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.4, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.5, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.6, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 0.8, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 1, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 1.2, verbose = FALSE)
mu_int_ife <- FindClusters(mu_int_ife, resolution = 1.5, verbose = FALSE)
```

## Save Object
```{r, eval = FALSE}
setwd("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/mu_int/")
saveRDS(mu_int_ife, file="mu_int_ife.Rds") 
```

## UMAPS colored by clusters
@different resolutions 

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8,1,1.2,1.5)
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new/plots")
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(mu_int_ife) = paste("integrated_snn_res.",res,sep="")
  png(paste("mu_int_ife_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(mu_int_ife, reduction="umap", label=T, do.return = T, pt.size = 0.25)
  print(p)
  dev.off()
}
```

## Feature Plots

```{r, eval = FALSE}
DefaultAssay(mu_int_ife) = "RNA"

genes = c("Krt14", "Krt5", "Krt1", "Krt10", "Lhx2", "Krt19", 
"Azgp1", "Krt15", "Sox9", "Cd14", "Cd207", "Cd3e", "Krt16", "Krt6a",
"Col1a1", "S100a8", "S100a9", "Mgst1", "Apoe", 
"Xcl1", "Mki67", "Dio2", "Wif1", "Krt15", 
"Col17a1", "Flg", "Cd34", "Itga6", "Col17a1", "Itgb1", "Itgb4", 
"Barx2", "Msx2", "Krt25", "Krt27", "Krt71", "Krt79", "Pthlh", 
"Lgr5", "Lgr6", "Cst6", "Fgf5", "Krt31", "Sparc", "Dcn", "Corin", 
"Sfrp1", "Edn2", "Tagln","Des","Myh9","Krt35","Acta1",
"Ptn","Sostdc1","Dkk3","Tnc","Sfrp2","Lamb3", "Itgam","Itgax","Ptn","Sostdc1",
"Fcgbp","H2-M2","Epgn","Ivl","H2-Aa","Cd74","S100a1","Pcna","Wnt10a")

genes_match = genes[genes %in% rownames(mu_int_ife)]

for (i in 1:length(genes_match))
{
  png(paste("mu_int_ife_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = mu_int_ife, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Finding Cluster Markers

```{r, eval = FALSE}
Idents(mu_int_ife) = "integrated_snn_res.0.4"
setwd("/scratch/groups/khavari/users/andrewji/mu_all/integrated/mu_int_ife_new")
markers <- FindAllMarkers(mu_int_ife, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "mu_int_ife_seurat_markers_res0.4.csv",sep = ",",row.names = T, col.names=T)
```