---
title: "Integrating Human KCs"
author: "Larry Chen"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r load-packages, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
library(cowplot)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r, include = FALSE}
kc_int = readRDS('C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/kc_int/kc_int.Rds')
```

## Load data

```{r, eval = FALSE}
load("/oak/stanford/groups/khavari/users/andrewji/seurat_analysis/merge12ptsnew/merge12ptsnew_kc/kc_norm/kc_norm_update.Robj")

#kc <- CreateSeuratObject(kc.data, meta.data = metadata)
kc.list <- SplitObject(kc_norm_update, split.by = "patient")

for (i in 1:length(kc.list)) {
    kc.list[[i]] <- NormalizeData(kc.list[[i]], verbose = FALSE)
    kc.list[[i]] <- FindVariableFeatures(kc.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

## Integrate data

```{r, eval = FALSE}
# Try 7 patients with cells > 700 in dataset
reference.list <- kc.list[c("P1","P2","P5","P6","P7","P9","P10")]
kc.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

kc_int <- IntegrateData(anchorset = kc.anchors, dims = 1:30)
DefaultAssay(kc_int) <- "integrated"
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
kc_int <- ScaleData(kc_int, verbose = FALSE)
kc_int <- RunPCA(kc_int, npcs = 30, verbose = FALSE)
kc_int <- RunUMAP(kc_int, reduction = "pca", dims = 1:30)
```

## Patient/Subpop UMAPs

```{r, eval = FALSE}
p1 <- DimPlot(kc_int, reduction = "umap", group.by = "patient")
p2 <- DimPlot(kc_int, reduction = "umap", group.by = "subpop", label = TRUE, 
    repel = TRUE) + NoLegend()
p = plot_grid(p1, p2)

png("kc_int_pt7_labelbypatient_subpop.png", units = "in", height = 5, width = 10, res=300)
print(p)
dev.off()
```

```{r, echo = FALSE}
p1 <- DimPlot(kc_int, reduction = "umap", group.by = "patient")
p2 <- DimPlot(kc_int,reduction = "umap", group.by = "subpop", label = TRUE, 
    repel = TRUE) + NoLegend()
plot_grid(p1, p2)
```

## Clustering

```{r, eval = FALSE}
kc_int <- FindNeighbors(kc_int, dims = 1:30, verbose = T)
kc_int <- FindClusters(kc_int, resolution = 0.1, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.15, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.2, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.25, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.3, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.4, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.6, verbose = FALSE)
kc_int <- FindClusters(kc_int, resolution = 0.8, verbose = FALSE)
```

## Graphing

### Generate UMAPS

At resolutions 0.1, 0.15, 0.2, 0.25, 0.3, 0.4, 0.6, and 0.8, using the integrated assay

```{r, eval = FALSE}
all_res = c(0.1,0.15,0.2,0.25,0.3,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
	res = all_res[i]
	Idents(kc_int) = paste("integrated_snn_res.",res,sep="")
	png(paste("kc_int_res",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
	p=DimPlot(kc_int, reduction="umap", label=T, do.return = T, pt.size = 1)
	print(p)
	dev.off()
}
```

### Feature Plots

```{r, eval = FALSE}
genes = c("ITGA6","ITGB1","ITGA2","ITGA3","ODC1","FOSL1","HAS3","PLAU","PHLDA1","PHLDA2","COL17A1","MMP10","PTHLH","MMP1","KRT1",
	"MKI67","ZNF750","ASS1","POSTN","HELLS","RRM2","PTTG1","IVL","TGM3","LOR")
genes = c("KRT14","KRT15","KRT5")
for (i in 1:length(genes))
{
  png(paste("kc_int_",genes[i],"_noaxes_nolegend_pt1.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = kc_int, features = genes[i], cols = c("lightgrey", "blue"), pt.size = 1)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Calculate Cell Cycle Scores

```{r, eval = FALSE}
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes
kc_int <- CellCycleScoring(kc_int, s.features = s.genes, g2m.features = g2m.genes, set.ident = TRUE)
```

### Plot Cell Cycle Scores

```{r, eval = FALSE}
p1 <- DimPlot(kc_int, reduction = "umap")


png("kc_int_pt7_cc_phase.png", units = "in", height = 5, width = 5, res=300)
print(p1)
dev.off()
```

```{r, echo = FALSE}
Idents(kc_int) = 'Phase'
DimPlot(kc_int, reduction = "umap")
```

## Find Markers

### At resolution 0.1

```{r, eval = FALSE}
### AT res 0.1
Idents(kc_int) = "integrated_snn_res.0.1"

markers <- FindAllMarkers(kc_int, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj <0.05)
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/merge12ptsnew_kc/kc_norm/kc_int")
write.table(markers.filt,file="kc_int_seurat_markers_res0.1.txt",sep = "\t",row.names = T,col.names = T)
```

### At resolution 0.6

```{r, eval = FALSE}
### AT res 0.6
Idents(kc_int) = "integrated_snn_res.0.6"

markers <- FindAllMarkers(kc_int, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj <0.05)
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/merge12ptsnew_kc/kc_norm/kc_int")
write.table(markers.filt,file="kc_int_seurat_markers_res0.6.txt",sep = "\t",row.names = T,col.names = T)
```

## Gene violin plots

```{r, eval = FALSE}
genes = c("ITGA6","ITGB1","ITGA2","ITGA3","ODC1","FOSL1","HAS3","PLAU","PHLDA1","PHLDA2","COL17A1","MMP10","PTHLH","MMP1","KRT1",
	"MKI67","ZNF750","ASS1","POSTN","HELLS","RRM2","PTTG1","IVL","TGM3","LOR","SLURP1","CALML5","KRT14","KRT15","KRT5")
for (i in 1:length(genes))
{
  pdf(paste("kc_int_",genes[i],"_noaxes_nolegend_vlnplot.pdf",sep=""), height = 3, width = 6)
  p=VlnPlot(object = kc_int, features = genes[i], pt.size = 0)
  #p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/merge12ptsnew_kc/kc_norm/kc_int")
saveRDS(kc_int,file="kc_int.Rds")
```
