---
title: "Generating norm_update"
author: "Larry Chen"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r load-packages, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
library(cowplot)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-upload, include = FALSE}
ns_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int.Rds")
```

## Load ns_int

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/norm")
ns_int = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int.Rds")
```

### Subset ns_int to create norm_update

```{r}
Idents(ns_int) = 'dataset'
norm_update = subset(ns_int, idents = "AJ")
```

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/norm/plots")
Idents(norm_update) = "patient"
patient_order = c("P1","P2","P3","P4","P5","P6","P7","P8","P9","P10")
Idents(norm_update) = factor(x = Idents(norm_update), levels = patient_order)
png("norm_update_labelbypatient.png", units = "in", height = 5, width = 6, res=300)
DimPlot(norm_update, reduction="umap", do.label=F, do.return = T, pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
Idents(norm_update) = "patient"
patient_order = c("P1","P2","P3","P4","P5","P6","P7","P8","P9","P10")
Idents(norm_update) = factor(x = Idents(norm_update), levels = patient_order)
DimPlot(norm_update, reduction="umap", pt.size = 0.1)
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
all.genes <- rownames(norm_update)
norm_update <- ScaleData(norm_update, features = all.genes, vars.to.regress = c("nCount_RNA","percent.mt"))
norm_update <- RunPCA(norm_update, features = VariableFeatures(object = norm_update))
norm_update <- RunUMAP(norm_update, dims = 1:15, verbose = TRUE)
```

## Clustering

```{r, eval = FALSE}
norm_update <- FindNeighbors(norm_update, dims = 1:15, verbose = FALSE)
norm_update <- FindClusters(norm_update, resolution = 0.4, verbose = FALSE)
```

## Graphing

### Feature Plots

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/10xdata/merge12ptsnew/norm/plots")
genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207","CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1")
for (i in 1:length(genes))
{
  png(paste("norm_update_",genes[i],"_noaxes_nolegend_pt0.25_norp.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = norm_update, features = genes[i], cols = c("lightgrey", "blue"), pt.size = 0.25)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

### UMAPs

#### color by final cell

```{r, eval = FALSE}
png("norm_update_labelbybfinalcell_norp.png", units = "in", height = 5, width = 7.5, res=300)
DimPlot(norm_update, reduction="umap", do.label=F, group.by = "finalcell", do.return = T, pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
DimPlot(norm_update, reduction="umap", group.by = "finalcell", pt.size = 0.1)
```

#### color by res.0.4 clusters

```{r, eval = FALSE}
png("norm_update_res.0.4_norp.png", units = "in", height = 5, width = 6, res=300)
DimPlot(norm_update, reduction="umap", do.label=T, do.return = T, pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
Idents(norm_update) = 'integrated_snn_res.0.4'
DimPlot(norm_update, reduction="umap", pt.size = 0.1)
```

#### color by patient

```{r, eval = FALSE}
Idents(norm_update) = "patient"
patient_order = c("P1","P2","P3","P4","P5","P6","P7","P8","P9","P10")
Idents(norm_update) = factor(x = Idents(norm_update), levels = patient_order)
png("norm_update_labelbypatient_norp.png", units = "in", height = 5, width = 6, res=300)
DimPlot(norm_update, reduction="umap", do.label=F, do.return = T, pt.size = 0.1)
dev.off()
```

```{r, echo = FALSE}
Idents(norm_update) = "patient"
patient_order = c("P1","P2","P3","P4","P5","P6","P7","P8","P9","P10")
Idents(norm_update) = factor(x = Idents(norm_update), levels = patient_order)
DimPlot(norm_update, reduction="umap", pt.size = 0.1)
```

#### color by nCount_RNA

```{r, eval = FALSE}
png("norm_update_nUMI_norp.png", units = "in", height = 6, width = 5, res=300)
p=FeaturePlot(object = norm_update, features = "nCount_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
p = p + NoLegend() + NoAxes()
print(p)
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(object = norm_update, features = "nCount_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
```

## Save Object

```{r, eval = FALSE}
setwd("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/kc_int")
saveRDS(norm_update, file="norm_update.Rds") 
```
