---
title: "Removing doublets from human PSU cells (FINAL STEP)"
author: "Larry Chen"
date: "2023-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

## Import Libraries

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
ns_int_psu_ref = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_psu_ref.Rds")
```

## Read Object

```{r, eval = FALSE}
ns_int_psu_filt = readRDS("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/ns_int_psu_filt.Rds")
DefaultAssay(ns_int_psu_filt) = "RNA"
```

## Remove inferred doublets

```{r, eval = FALSE}
Idents(ns_int_psu_filt) = "integrated_snn_res.0.8"

# Filter out cluster 14, which are inferred doublets
ns_int_psu_ref = subset(ns_int_psu_filt, idents = c(0:13,15:17))
```

## Preprocessing

```{r, eval = FALSE}
ns.list <- SplitObject(ns_int_psu_ref, split.by = "sample")

#x=which(table(ns_int_psu_ref$sample)>84)
#sample_keep = names(table(ns_int_psu_ref$sample)[x])
# sample_keep = c("abd4", "br41epi", "br53epi", "P1", "P10", "P2", "P5", "P6", "P3",
# "P7", "P9", "rt1","rt2", "s11", "SC1control", "SC18control", "SC32control", "SC33control", "SC34control", "SC4control","scalp26", 
# "scalp32")

#ns.list = ns.list[sample_keep]

for (i in 1:length(ns.list)) {
    ns.list[[i]] <- NormalizeData(ns.list[[i]], verbose = FALSE)
    ns.list[[i]] <- FindVariableFeatures(ns.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

## Integration

```{r, eval = FALSE}
reference.list <- ns.list
ns.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30, k.filter = 85)

ns_int_psu_ref <- IntegrateData(anchorset = ns.anchors, dims = 1:30)
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
DefaultAssay(ns_int_psu_ref) <- "integrated"
ns_int_psu_ref <- ScaleData(ns_int_psu_ref, verbose = FALSE)
ns_int_psu_ref <- RunPCA(ns_int_psu_ref, npcs = 30, verbose = FALSE)
ns_int_psu_ref <- RunUMAP(ns_int_psu_ref, reduction = "pca", dims = 1:30)
```

## Clustering

```{r, eval = FALSE}
ns_int_psu_ref <- FindNeighbors(ns_int_psu_ref, dims = 1:30, verbose = T)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.1, verbose = FALSE)
#ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.15, verbose = FALSE)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.2, verbose = FALSE)
#ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.25, verbose = FALSE)
#ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.3, verbose = FALSE)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.4, verbose = FALSE)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.6, verbose = FALSE)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 0.8, verbose = FALSE)
ns_int_psu_ref <- FindClusters(ns_int_psu_ref, resolution = 1, verbose = FALSE)
```

## UMAPS

### By orig.ident

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/ns_int_psu_ref/plots")

png("ns_int_psu_ref_labelby_origident.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "orig.ident", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "orig.ident", pt.size = 0.25)
```

### By sample

```{r, eval = FALSE}
png("ns_int_psu_ref_labelby_sample.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "sample", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "sample", pt.size = 0.25)
```

### By subcell

```{r, eval = FALSE}
png("ns_int_psu_ref_labelby_subcell.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "subcell", pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_ref, reduction="umap", label=F, group.by = "subcell", pt.size = 0.25)
```

### by select subcells

```{r}
Idents(ns_int_psu_ref) = "subcell"
subcell_order = c("OB", "IB", "SB", "PS_Cyc", "Inf_II", "Inf_III", 
"Inf_IV", "Spn_I", "Inf_I", "Spn_IFN", 
"Spn_III", "Cyc_I", "Spn_II", "Bas_I", "Basal_III", 
"Bas_II", "SG_I", "Cyc_III", "IRS", 
"SG_II")
cells_highlight = WhichCells(ns_int_psu_ref, idents = subcell_order)
```

```{r, eval = FALSE}
png("ns_int_psu_ref_labelby_subcell_noNA_label.png", units = "in", height = 5, width = 8, res=300)
DimPlot(ns_int_psu_ref, reduction = "umap",cells = cells_highlight, label=T, pt.size = 0.25)
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_ref, reduction = "umap",cells = cells_highlight, label=T, pt.size = 0.25)
```

### By clusters

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8,1)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(ns_int_psu_ref) = paste("integrated_snn_res.",res,sep="")
  png(paste("ns_int_psu_ref_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(ns_int_psu_ref, reduction="umap", label=T, do.return = T, pt.size = 0.25)
  print(p)
  dev.off()
}
```

```{r, echo = FALSE}
Idents(ns_int_psu_ref) = "integrated_snn_res.1"
DimPlot(ns_int_psu_ref, reduction="umap", label=T, do.return = T, pt.size = 0.25)
```

## Feature Plots

```{r, eval = FALSE}
DefaultAssay(ns_int_psu_ref) = "RNA"

genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207",
  "CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1",
  "KRT23","KRT25","KRT6A","KRT16","KRT17","PPARG","DIO2","COMP","FGF7","COL17A1","TP63","PTN","SAT1","SOX4","KLF5","TNC",
  "PTHLH","MT1X","MT1G","MT1H","MT1E","SFRP1","DMKN","ZNF750","IVL","SOSTDC1","FGF18","IL37","IL1F10","IL36RN","IL1RN",
  "MDK","LGALS1","CD151","ITGB1","MKI67","LUM","COL6A1","SOX2","DHRS9","LCE1E","PIP",
  "S100P","MMP7","KRT77","FZD10","PCDH19","DLX3","ANGPTL7","PARM1","KRT8","KRT18","CD200","CD59","FST",
  "MSX2","BARX2","IL11RA","LGR5","LGR6","FGF5","EDN2","CST6","KRT79", "CD34","PTN",
  "RUNX3","HAS1","RUNX2","GJB6","GJB2","AQP5","KRT7","TMEM213","KIF12","TSPAN18","MFAP2","CLDN10","FAM13A","ID1","ID3",
  "KRT7","TMEM213","KRT75","TP63","SOX2","CORIN","PROM1","NRG2","CNTN1","ENPP1","DACT1","SBSPON","BDNF","VIM",
  "BPIFC","SPON2","GPX3","WFDC18","EPCAM","PRDM1","ASPN","TGFB1","TGFB2","TGFB3","S100A2","MGP","RARRES2",
  "S100A3","KRT35","KRT85","PRR9","TCHH","KRT28","FABP9","DAPL1","DSG4","DSC1","CXCL14",
  "KRT34","KRT71","HOXC13","KRT81","KRT82","KRT83","KRTAP11-1","GSDMA","KRT40","KRT31","KRT72","KRT73","KRTAP24-1",
  "AWAT2","PPARG","ELOVL3","ELOVL5","RPTN","AWAT1","ACSL1","LRIG1")
genes_match = genes[genes %in% rownames(ns_int_psu_ref)]

for (i in 1:length(genes_match))
{
  png(paste("ns_int_psu_ref_",genes_match[i],"_noaxes_nolegend_pt0.25_RNA.png",sep=""), units = "in", height = 5, width = 5, res=300)
  p=FeaturePlot(object = ns_int_psu_ref, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoAxes()
  print(p)
  dev.off()
}
```

## Save object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/ns_int_psu_ref/")
saveRDS(ns_int_psu_ref, file="ns_int_psu_ref.Rds") 
```

## Find Markers

```{r, eval = FALSE}
Idents(ns_int_psu_ref) = "integrated_snn_res.0.6"
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/ns_int_psu_ref/")

markers <- FindAllMarkers(ns_int_psu_ref, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_psu_ref_seurat_markers_res0.6.csv",sep = ",",row.names = T, col.names=T)

Idents(ns_int_psu_ref) = "integrated_snn_res.0.8"
markers <- FindAllMarkers(ns_int_psu_ref, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_psu_ref_seurat_markers_res0.8.csv",sep = ",",row.names = T, col.names=T)

Idents(ns_int_psu_ref) = "integrated_snn_res.1"
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/ns_int_psu_ref/")

markers <- FindAllMarkers(ns_int_psu_ref, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_psu_ref_seurat_markers_res1.csv",sep = ",",row.names = T, col.names=T)
```
