---
title: "Filtering human PSU cells"
author: "Larry Chen"
date: "2023-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

## Import Libraries

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
#ns_int_psu_filt = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_psu_filt.Rds")
```

## Load Object

```{r, eval = FALSE}
ns_int_psu_noecc = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_psu_noecc.Rds")
DefaultAssay(ns_int_psu_noecc) = "RNA"
```

## Filter Out Fibroblasts

We filter out a cluster of Fibroblast cells, which were identified when we ran Seurat's clustering algorithm on the RNA assay, \@ resolution 0.6. This process is outlined in the 'ns_int_psu_noecc_trad_norm_121020' markdown.

```{r, eval = FALSE}
Idents(ns_int_psu_noecc) = "RNA_snn_res.0.6"

# Filter out cluster 5, which are fibroblasts
ns_int_psu_filt = subset(ns_int_psu_noecc, idents = c(0:4,6:17))
```

## Split object/selecting samples

Only keeping samples with more than 84 cells.

```{r, eval = FALSE}
ns.list <- SplitObject(ns_int_psu_filt, split.by = "sample")

x=which(table(ns_int_psu_filt$sample)>84)
sample_keep = names(table(ns_int_psu_filt$sample)[x])

# sample_keep = c("abd4", "br41epi", "br53epi", "P1", "P10", "P2", "P5", "P6", "P3",
# "P7", "P9", "rt1","rt2", "s11", "SC1control", "SC18control", "SC32control", "SC33control", "SC34control", "SC4control","scalp26", 
# "scalp32")
```

## Preprocessing

```{r, eval = FALSE}
ns.list = ns.list[sample_keep]

for (i in 1:length(ns.list)) {
    ns.list[[i]] <- NormalizeData(ns.list[[i]], verbose = FALSE)
    ns.list[[i]] <- FindVariableFeatures(ns.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

## Integration

```{r, eval = FALSE}
reference.list <- ns.list
ns.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30, k.filter = 85)

ns_int_psu_filt <- IntegrateData(anchorset = ns.anchors, dims = 1:30)
```

```{r, eval = FALSE}
DefaultAssay(ns_int_psu_filt) <- "integrated"
ns_int_psu_filt <- ScaleData(ns_int_psu_filt, verbose = FALSE)
ns_int_psu_filt <- RunPCA(ns_int_psu_filt, npcs = 30, verbose = FALSE)
ns_int_psu_filt <- RunUMAP(ns_int_psu_filt, reduction = "pca", dims = 1:30)
```

## Clustering

```{r, eval = FALSE}
ns_int_psu_filt <- FindNeighbors(ns_int_psu_filt, dims = 1:30, verbose = T)
ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.1, verbose = FALSE)
#ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.15, verbose = FALSE)
ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.2, verbose = FALSE)
#ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.25, verbose = FALSE)
#ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.3, verbose = FALSE)
ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.4, verbose = FALSE)
ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.6, verbose = FALSE)
ns_int_psu_filt <- FindClusters(ns_int_psu_filt, resolution = 0.8, verbose = FALSE)
```

## UMAPS

### By orig.ident

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/plots")

png("ns_int_psu_filt_labelby_origident.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", do.label=F, group.by = "orig.ident", do.return = T, pt.size = 0.25)
dev.off()
```

### By sample

```{r, eval = FALSE}
png("ns_int_psu_filt_labelby_sample.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", do.label=F, group.by = "sample", do.return = T, pt.size = 0.25)
dev.off()
```

### By integrated_snn_res.0.2

```{r, eval = FALSE}
png("ns_int_psu_filt_res.0.2.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", label=T, group.by = "integrated_snn_res.0.2", pt.size = 0.1)
dev.off()
```

### By integrated_snn_res.0.4

```{r, eval = FALSE}
png("ns_int_psu_filt_res.0.4.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", label=T,  group.by = "integrated_snn_res.0.4", pt.size = 0.1)
dev.off()
```

### By integrated_snn_res.0.6

```{r, eval = FALSE}
png("ns_int_psu_filt_res.0.6.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", label=T,  group.by = "integrated_snn_res.0.6", pt.size = 0.1)
dev.off()
```

### By integrated_snn_res.0.8

```{r, eval = FALSE}
png("ns_int_psu_filt_res.0.8.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", label=T, group.by = "integrated_snn_res.0.8", pt.size = 0.1)
dev.off()
```

### By integrated_snn_res.1

```{r, eval = FALSE}
png("ns_int_psu_filt_res.1.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_filt, reduction="umap", label=T, group.by = "integrated_snn_res.1", pt.size = 0.1)
dev.off()
```

### By nCount_RNA

```{r, eval = FALSE}
png("ns_int_psu_filt_nUMI.png", units = "in", height = 5, width = 5, res=300)
p=FeaturePlot(object = ns_int_psu_filt, features = "nCount_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
p = p + NoAxes()
print(p)
dev.off()
```

### By nFeature_RNA

```{r, eval = FALSE}
png("ns_int_psu_filt_nFeature.png", units = "in", height = 5, width = 5, res=300)
p=FeaturePlot(object = ns_int_psu_filt, features = "nFeature_RNA", cols = c("lightgrey", "blue"), pt.size = 0.25)
p = p + NoAxes()
print(p)
dev.off()
```

## Feature plots

```{r, eval = FALSE}
genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207",
  "CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1",
  "KRT23","KRT25","KRT6A","KRT16","KRT17","PPARG","DIO2","COMP","FGF7","COL17A1","TP63","PTN","SAT1","SOX4","KLF5","TNC",
  "PTHLH","MT1X","MT1G","MT1H","MT1E","SFRP1","DMKN","ZNF750","IVL","SOSTDC1","FGF18","IL37","IL1F10","IL36RN","IL1RN",
  "MDK","LGALS1","CD151","ITGB1","MKI67","LUM","COL6A1","SOX2","DHRS9","LCE1E","PIP",
  "S100P","MMP7","KRT77","FZD10","PCDH19","DLX3","ANGPTL7","PARM1","KRT8","KRT18","CD200","CD59","FST",
  "MSX2","BARX2","IL11RA","LGR5","LGR6","FGF5","EDN2","CST6","KRT79", "CD34","PTN",
  "RUNX3","HAS1","RUNX2","GJB6","GJB2","AQP5","KRT7","TMEM213","KIF12","TSPAN18","MFAP2","CLDN10","FAM13A","ID1","ID3",
  "KRT7","TMEM213","KRT75","TP63","SOX2","CORIN","PROM1","NRG2","CNTN1","ENPP1","DACT1","SBSPON","BDNF")
genes_match = genes[genes %in% rownames(ns_int_psu_filt)]
DefaultAssay(ns_int_psu_filt) = 'RNA'
for (i in 1:length(genes_match))
{
  png(paste("ns_int_psu_filt_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = ns_int_psu_filt, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
DefaultAssay(ns_int_psu_filt) = 'integrated'
```

## QC violin plot

```{r, eval = FALSE}
pdf("ns_int_psu_filt_nCount_Feature.pdf",height=4,width=6)
VlnPlot(ns_int_psu_filt,features = c("nCount_RNA","nFeature_RNA"), group.by = "sample")
dev.off()
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu/ns_int_psu_filt/")
saveRDS(ns_int_psu_filt, file="ns_int_psu_filt.Rds") 
```

## Find Markers

```{r, eval = FALSE}
Idents(ns_int_psu_filt) = "integrated_snn_res.0.8"
markers <- FindAllMarkers(ns_int_psu_filt, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_psu_filt_seurat_markers_res0.8.csv",sep = ",",row.names = T, col.names=T)
```
