---
title: "Isolating human PSU cells"
author: "Larry Chen"
date: "2023-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NOTE: This code utilizes Seurat v3.0.0. You will need to install seurat version 3.0.0 using 'remotes'. We recommend installing the version in separate location from your regular seurat package.

```{r install-seurat3.0.0, eval = FALSE}
remotes::install_version('Seurat', version = '3.0.0', lib = "C:/Users/Ji Lab/AppData/Local/R/alt_packages" )
```

```{r, message = FALSE}
Sys.setenv(RETICULATE_PYTHON = "C:/Users/Ji Lab/AppData/Local/Programs/Python/Python310")
library(reticulate)
library(Seurat, lib.loc = "C:/Users/Ji Lab/AppData/Local/R/alt_packages")
library(dplyr)
library(ggplot2)
```

```{r session-info}
sessioninfo::session_info()%>%
  details::details(
    summary = 'Current session info',
    open    = TRUE
  )
```

```{r secret-load, include = FALSE}
ns_int_psu_noecc = readRDS("C:/Users/Ji Lab/Documents/JID manuscript/andrew_scripts/orig_obj/ns_int_psu_noecc.Rds")
```

## Load Object

```{r, eval = FALSE}
ns_int = readRDS("/scratch/groups/khavari/users/andrewji/ns_int/ns_int.Rds")
DefaultAssay(ns_int) = "RNA"
```

## Subset object

Remove eccrine cells

```{r, eval = FALSE}
res = 0.6
Idents(ns_int) = paste("integrated_snn_res.",res,sep="")
ns_int_psu_noecc = subset(ns_int, idents = c(7,8,12,14,19,20))
```

## Split objects and choose samples

```{r, eval = FALSE}
ns.list <- SplitObject(ns_int_psu_noecc, split.by = "sample")

#x=which(table(ns_int_psu_noecc$sample)>120)
sample_keep = c("abd4", "br41epi", "br53epi", "P1", "P10", "P2", "P5", "P6", "P3",
"P7", "P9", "rt1","rt2", "s11", "SC1control", "SC18control", "SC32control", "SC33control", "SC34control", "SC4control","scalp26", 
"scalp32")
ns.list = ns.list[sample_keep]
```

## Preprocessing

```{r, eval = FALSE}
for (i in 1:length(ns.list)) {
    ns.list[[i]] <- NormalizeData(ns.list[[i]], verbose = FALSE)
    ns.list[[i]] <- FindVariableFeatures(ns.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}
```

## Integrate

```{r, eval = FALSE}
reference.list <- ns.list
ns.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30, k.filter = 85)

ns_int_psu_noecc <- IntegrateData(anchorset = ns.anchors, dims = 1:30)
```

## Scale/PCA/UMAP

```{r, eval = FALSE}
DefaultAssay(ns_int_psu_noecc) <- "integrated"
ns_int_psu_noecc <- ScaleData(ns_int_psu_noecc, verbose = FALSE)
ns_int_psu_noecc <- RunPCA(ns_int_psu_noecc, npcs = 30, verbose = FALSE)
ns_int_psu_noecc <- RunUMAP(ns_int_psu_noecc, reduction = "pca", dims = 1:30)
```

## Clustering

```{r, eval = FALSE}
ns_int_psu_noecc <- FindNeighbors(ns_int_psu_noecc, dims = 1:30, verbose = T)
ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.1, verbose = FALSE)
#ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.15, verbose = FALSE)
ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.2, verbose = FALSE)
#ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.25, verbose = FALSE)
#ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.3, verbose = FALSE)
ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.4, verbose = FALSE)
ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.6, verbose = FALSE)
ns_int_psu_noecc <- FindClusters(ns_int_psu_noecc, resolution = 0.8, verbose = FALSE)
```

## Save Object

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu_noecc")
saveRDS(ns_int_psu_noecc, file="ns_int_psu_noecc.Rds") 
```

## UMAPS

### By sample

```{r, eval = FALSE}
setwd("/scratch/groups/khavari/users/andrewji/ns_int/ns_int_psu_noecc/plots")
png("ns_int_psu_noecc_labelby_sample.png", units = "in", height = 5, width = 8, res=300)
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "sample")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "sample")
```

### By dataset

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_dataset.png", units = "in", height = 5, width = 6, res=300)
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "dataset")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "dataset")
```

### By subcell

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_subcell.png", units = "in", height = 5, width = 8, res=300)
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "subcell")
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_noecc, reduction = "umap", group.by = "subcell")
```

### By percent.mt

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_percentmt.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_psu_noecc, features = "percent.mt")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_psu_noecc, features = "percent.mt")
```

### By nCount_RNA

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_nUMI.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_psu_noecc, features = "nCount_RNA")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_psu_noecc, features = "nCount_RNA")
```

### By nFeature_RNA

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_nFeature.png", units = "in", height = 5, width = 5, res=300)
FeaturePlot(ns_int_psu_noecc, features = "nFeature_RNA")
dev.off()
```

```{r, echo = FALSE}
FeaturePlot(ns_int_psu_noecc, features = "nFeature_RNA")
```

### Highlight subcell types

#### Choose subcell types to highlight

```{r}
#Idents(ns_int_psu) = "subcell"
subcell_order = c("HF", "Inf_II", "Inf_III", "Inf_IV", "PS_Cyc", "Spn_IFN", "Keratinocyte", 
"MDSC", "SG_I", "Multiplet", "Spn_I", "Inf_I", "Multi", "Cyc_I", 
"IB", "Spn_II", "Basal_III", "Spn_III", "SB", "OB", "IRS", 
"Cyc_III", "SG_II", "Bas_II", "Fibroblast", "N_Cyc", "Bas_I", 
"Endothelial Cell")
```

```{r, eval = FALSE}
Idents(ns_int_psu_noecc) = "subcell"
cells_highlight = WhichCells(ns_int_psu_noecc, idents = subcell_order)
png("ns_int_psu_noecc_labelby_subcell_noNA.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_noecc, reduction = "umap",cells = cells_highlight)
dev.off()
```

```{r, echo = FALSE}
Idents(ns_int_psu_noecc) = "subcell"
cells_highlight = WhichCells(ns_int_psu_noecc, idents = subcell_order)
DimPlot(ns_int_psu_noecc, reduction = "umap", cells = cells_highlight)
```

```{r, eval = FALSE}
png("ns_int_psu_noecc_labelby_subcell_noNA_label.png", units = "in", height = 5, width = 7, res=300)
DimPlot(ns_int_psu_noecc, reduction = "umap",cells = cells_highlight, label=T)
dev.off()
```

```{r, echo = FALSE}
DimPlot(ns_int_psu_noecc, reduction = "umap", cells = cells_highlight, label=T)
```

### By cluster

```{r, eval = FALSE}
all_res = c(0.1,0.2,0.4,0.6,0.8)
for (i in 1:length(all_res))
{
  res = all_res[i]
  Idents(ns_int_psu_noecc) = paste("integrated_snn_res.",res,sep="")
  png(paste("ns_int_psu_noecc_res_",res,".png",sep=""), units = "in", height = 5, width = 5.5, res=300)
  p=DimPlot(ns_int_psu_noecc, reduction="umap", label=T, do.return = T, pt.size = 0.1)
  print(p)
  dev.off()
}
```

```{r, echo = FALSE}
Idents(ns_int_psu_noecc) = 'integrated_snn_res.0.4'
DimPlot(ns_int_psu_noecc, reduction="umap", label=T, do.return = T, pt.size = 0.1)
```

## Feature Plots

```{r, eval = FALSE}
genes = c("KRT14","KRT5","KRT1","KRT10","LHX2","KRT19","AZGP1","KRT15","SOX9","CD14","CD163","CD207",
	"CD3E","MLANA","VWF","COL1A1","S100A8","S100A9","CD1C","CLEC9A","MGST1","APOE","XCL1",
	"KRT23","KRT25","KRT6A","KRT16","KRT17","PPARG","DIO2","COMP","FGF7","COL17A1","TP63","PTN","SAT1","SOX4","KLF5","TNC",
	"PTHLH","MT1X","MT1G","MT1H","MT1E","SFRP1","DMKN","ZNF750","IVL","SOSTDC1","FGF18","IL37","IL1F10","IL36RN","IL1RN",
	"MDK","LGALS1","CD151","ITGB1","MKI67","LUM","COL6A1","SOX2","DHRS9","LCE1E","PIP","LGR5","LGR6","ANGPTL7","BGN","MDK",
	"KIF12","TSPAN18","MFAP2","CLDN10","FAM13A","ID1","ID3","KRT7","TMEM213","KRT75","TP63",
	"SOX2","CORIN","PROM1","NRG2","CNTN1","STX17","PRDX5","CD34","CST6","MSX2","BARX2","IL11RA","FGF5",
	"S100P","MMP7","KRT77","FZD10","PCDH19","DLX3","ANGPTL7","PARM1","KRT8","KRT18")

#genes = "MT-CYB"
genes_match = genes[genes %in% rownames(ns_int_psu_noecc)]
DefaultAssay(ns_int_psu_noecc) = 'RNA'

for (i in 1:length(genes_match))
{
  png(paste("ns_int_psu_noecc_",genes_match[i],"_noaxes_nolegend_pt0.25.png",sep=""), units = "in", height = 6, width = 5, res=300)
  p=FeaturePlot(object = ns_int_psu_noecc, features = genes_match[i], cols = c("lightgrey", "blue"), pt.size = 0.25, order=T)
  p = p + NoLegend() + NoAxes()
  print(p)
  dev.off()
}
```

## Find Markers

```{r, eval = FALSE}
Idents(ns_int_psu_noecc) = "integrated_snn_res.0.6"
markers <- FindAllMarkers(ns_int_psu_noecc, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
markers.filt = subset(markers, p_val_adj < 0.05)
write.table(markers.filt, file = "ns_int_psu_noecc_seurat_markers_res0.6.csv",sep = ",",row.names = T, col.names=T)
```
